### 2022-09-22 paper.tex
Abstract Update
First update

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a contributed volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}

% choose options for [] as required from the list
% in the Reference Guide

\usepackage{type1cm}        % activate if the above 3 fonts are
                            % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom

\usepackage{newtxtext}       % 
\usepackage{newtxmath}       % selects Times Roman as basic font

% see the list of further useful packages
% in the Reference Guide

\makeindex             % used for the subject index
                       % please use the style svind.ist with
                       % your makeindex program

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\DeclareUnicodeCharacter{2212}{-}
\DeclareUnicodeCharacter{22C5}{-}

\begin{document}

\title*{Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)} 
\titlerunning{Animal Life Cycle Algorithm (ALCA)}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{J. C. Felix-Saul, Mario García Valdez}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{J. C. Felix-Saul \at Tijuana Institute of Technology, Tijuana, Mexico, \email{name@email.address}
\and Mario García Valdez \at Tijuana Institute of Technology, Tijuana, Mexico, \email{name@email.address}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\abstract*{In previous work, we introduced an algorithm inspired by the biological Life Cycle of animal species, consisting of the stages: birth, growth, reproduction, and death. As in nature, population individuals grow older and age. In this algorithm's reproduction process, couples must match by mutual attraction, where sometimes individuals won't procreate offspring because of the mate's low appeal. As time passes, the environment kills its individuals either because of low fitness or age, causing occasional population extinction. When this condition presents, it is required to create a new population if evaluations are available and termination conditions are favorable to continue. Some alternatives we explored to restart this new population are the random generation of a new set of candidate solutions and the creation of a new set of candidate solutions based on either: a mix of elements from the best historically found candidate solutions set (Elite); the mutation with uniform modification from the Elite or the historically best-found solution (Champion); crossing the Champion with the Elite; the projection of the Elite towards the Champion; based on random use of the previous alternatives. In this paper, we present one of the most promising alternatives to solve population extinction caused by nature's pressure in the Life Cycle algorithm: the projection of the Elite towards the Champion, where we compare the results obtained with the latter and the random use of all the alternatives, using classic benchmark functions for optimization for comparison.}

\abstract{In previous work, we introduced an algorithm inspired by the biological Life Cycle of animal species, consisting of the stages: birth, growth, reproduction, and death. As in nature, population individuals grow older and age. In this algorithm's reproduction process, couples must match by mutual attraction, where sometimes individuals won't procreate offspring because of the mate's low appeal. As time passes, the environment kills its individuals either because of low fitness or age, causing occasional population extinction. When this condition presents, it is required to create a new population if evaluations are available and termination conditions are favorable to continue. Some alternatives we explored to restart this new population are the random generation of a new set of candidate solutions and the creation of a new set of candidate solutions based on either: a mix of elements from the best historically found candidate solutions set (Elite); the mutation with uniform modification from the Elite or the historically best-found solution (Champion); crossing the Champion with the Elite; the projection of the Elite towards the Champion; based on random use of the previous alternatives. In this paper, we present one of the most promising alternatives to solve population extinction caused by nature's pressure in the Life Cycle algorithm: the projection of the Elite towards the Champion, where we compare the results obtained with the latter and the random use of all the alternatives, using classic benchmark functions for optimization for comparison.}

%\keywords{Distributed Bioinspired Algorithms \and Genetic Algorithms \and Cloud Computing.}

\section{Introduction}
\label{sec:1}

Bio-inspired algorithms have been very successful when used to solve complex
optimization problems
\cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but as
their complexity increases so does the computing power required
\cite{ontiveros2018high}. One strategy to address this processing need is to
use distributed computing \cite{thain2005distributed}, or the resources
available in the cloud \cite{garcia2013there,eshratifar2019bottlenet} to help
find the solution. This strategy gives us elasticity to adjust (increase or
reduce) the computing power to achieve a balance according to the nature of the
problem.

One of the problems that we have identified in this research is that most
bio-inspired algorithms are designed with a traditionally sequential
perspective \cite{porto2018evolutionary,back1996evolutionary}, where each
process must wait for the previous task to finish before continuing. Some
architectures address this issue
\cite{valdez2021container,garcia2015evospace,merelo2016nodio}, what
distinguishes this proposal is the introduction of  an algorithm designed in its
entirety as a native solution in the cloud, fully distributed, where its
processes are executed in parallel and interaction takes place asynchronously. This technique makes it
easy to scale the computing power according to the complexity required by the
problem \cite{armbrust2010view}.

We designed our algorithm using observation, analysis, and abstraction in
nature to identify what most species in the animal kingdom have in common,
where individuals of a population that best adapt to the environment have
greater chances of survival, reproduction, and improvement of the species.
Imagining as if the task of writing these rules of evolution was in our hands,
questioning how we could solve it?

Like nature, we identified what most species have in common in the life cycle.
Our algorithm works on a constantly evolving population, experiencing the
stages that all living beings undergo \cite{read1968system}: being born,
growing up, reproducing, and dying, where each of these stages will be
processes (of our algorithm) that randomly affect the population individuals,
emulating the organic way.

The main contribution of the paper is to design and create a new algorithm with
the purpose to demonstrate that it is possible to evolve a population of
individuals, similar to a Genetic Algorithm (GA), using a distributed,
parallel, and asynchronous methodology by implementation and testing of the
algorithm.

We present the description of the following sections in our paper. First, we
introduce our algorithm inspired by the Life-Cycle of animal species in
% Please use capitalization consistently; I don't think this should go in Caps - JJ
section~\ref{section.proposal}, followed by our experimental configuration and
results in section~\ref{section.experiments}, we analyze and describe some of
our research findings in section~\ref{section.discussion}, and we finalize by
presenting some inferences based on our experiments' results in
section~\ref{section.conclusions}.

\section{Proposal}
\label{section.proposal}
% Always give a unique label
% and use \ref{<label>} for cross-references
% and \cite{<label>} for bibliographic references
% use \sectionmark{}
% to alter or adjust the section heading in the running head

Many of the publications with the most influence on our research
~\cite{valdez2021container,garcia2021event,merelo2016performance,merelo2016nodio}
propose a cloud-native optimization architecture that features population-based
algorithms. They present ideas such as those mentioned in Figure~\ref{fig.background},
which planted the seed of thought of our current paper.

\begin{figure}
    \centering
    \includegraphics[width=80mm]{img/fig1_background.pdf}
    \caption{These ideas planted the seed of thought in our algorithm proposal.} \label{fig.background}
    \end{figure}

Our main inspiration for this algorithm was born from the study and observation
of nature, where many successful optimization algorithms have previously found
their own. Our focus was not on a single animal species but all of them, using
general abstraction to identify what those species have in common.

Some questions in our train of thought were: How does nature work? Is evolution
real? How do we enforce natural selection in evolution? What is the role of the
attraction between couples on reproduction? How much of a factor is the
attraction's role in the evolution of the species? What is the role of death in
all of this? How much of an impact does death have on the evolution of a
species? How do we include those ideas into our algorithm?

In our analysis, we consider a broad animal spectrum, from bacteria to humans
and lions, finding our inspiration on the biological Life Cycle of the animal
species, which consists of several stages \cite{read1968system}: birth, growth,
reproduction, and death. As in nature, we intend to execute all these stages in
parallel and asynchronously on a population that evolves constantly. The
combination of those processes is what we call evolution.

One of the main challenges when designing the algorithm was how to capture the
essence of life by reflecting a population evolution?. In our minds, it was
clear this task requires a combination of simultaneous working forces that
influences the population improvement over time. Our strategy was simple:
divide and conquer, looking into the clouds. Enter cloud-computing: previous
cloud-computing algorithms have proven successful results working in
optimization problems \cite{valdez2021container,garcia2021event}.

We turned back to our genetic algorithms knowledge, mixed with our inspiration
and cloud computing, and designed the algorithm with the quest to divide the
processing workload among multiple computers. This strategy would also make it
possible to run our algorithm as a cloud service. Theoretically, one
consequence of the workload distribution is to obtain lower execution times.

This algorithm seeks to imitate the natural life cycle, where new individuals
are born at any moment and mature over time, where they age and suffer
mutations throughout their lives. In reproduction, couples match by mutual
attraction, and they may have offspring. Death can happen to everyone: from a
newborn to an aged adult, where the individual's fitness will impact their
longevity. The general model concept is shown in Figure~\ref{fig.proposal}. The general
flowchart for the Life-Cycle algorithm is described in Figure~\ref{fig.flowchart}.

\begin{figure}
    \centering
    \includegraphics[width=70mm]{img/fig2_proposal.pdf}
    \caption{Algorithm model inspired by the animal species' biological Life-Cycle.} \label{fig.proposal}
    \end{figure}

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig4_flowchart.pdf}
    \caption{Life-Cycle algorithm general flowchart.} \label{fig.flowchart}
% Several terms are introduced here that are not defined in the text, like "champion list" and "attraction" - JJ
    \end{figure}

\subsection{Birth}

This algorithm starts with a randomly generated population, where the processes
will interact with the population independently. This means that at any given
time, any individual can experience any of these processes. Birth is the first
process of our algorithm, and it is responsible for the initial generation of
individuals.

\subsection{Growth}

As in nature, all individuals constantly grow, mature, or age. With increasing
age, individuals may lose strength but also gain more knowledge to solve
problems. We represent this with a possible mutation in each increment of age.
The growth process will take an individual to assess whether it's ready to
mature and undergo changes. % Not learning?  JJ

\subsection{Reproduction}

The attraction of a couple will depend on fitness: the better individual's
fitness, the more attractive it will be, making it easier to find mating
matches. This process will be taking random pairs of individuals to evaluate
their attraction as a couple, to try to breed; when the gestation is
successful, a new pair of individuals will be born (as the offspring). Not all
couples will be compatible, so reproduction will not always be possible, but
the problem arises: how to quantify the attraction between two individuals?

We could have used several strategies to evaluate this attraction. Considering
this algorithm takes a similar focus as the study of bacteria growth in
microbiology, where we can observe and analyze the evolution of a population
over time. As in nature' most species, the bigger a specimen is, the more
attractive it is to its mating candidates. To be consistent with both ideas in
% Er... not really. It depends on health, mainly - JJ
our algorithm, we use the equation of Newton's Law of Universal Gravitation (1)
to calculate the attraction between two individuals, where we visualize the
individual fitness as its mass when using the equation. In previous work,
Newton's Law of Universal Gravitation has shown success in helping to solve
optimization problems \cite{sanchez2014fuzzy,rashedi2009gsa}.

\begin{figure}
    \centering
    \includegraphics[width=50mm]{img/fig3_newtonslaw.pdf}
    \caption{Newton's Law of Universal Gravitation.} \label{fig.newtonslaw}
    \end{figure}

Where:
\begin{itemize}
    \item[]	    F is the gravitational force acting between two objects.
    \item[]	    m1 and m2 are the masses of the objects.
    \item[]	    r is the distance between the centers of their masses.
    \item[]	    G is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2.
\end{itemize}

% to be honest, I find this a bit far fetched. How do you define mass? is it related to fitness? - JJ

\subsection{Death}

The death stage represents the challenges and adversities that life presents to
overcome. This process evaluates the individual resistance to survive in the
environment. The better fitness the individual has will increase its chances of
survival. As time progresses, the demands of nature will also increase, pushing
for only the best individuals to survive.

\section{Experiments}
\label{section.experiments}

As a proof-of-concept, we implemented the algorithm with Docker containers by
solving the OneMax problem to compare it with a traditional GA algorithm using
the DEAP (Distributed Evolutionary Algorithms in Python) library
\cite{fortin2012deap}. The OneMax problem \cite{krejca2020lower,witt2019upper}
uses a genetic algorithm to evolve a population of randomly generated
individuals with zeros and ones, and it stops until a solution of only ones is
found.

\subsection{Experimental Setup}

\begin{figure}
    \includegraphics[width=\textwidth]{img/fig5_processes_containers.pdf}
    \caption{Life-Cycle algorithm processes in containers comparison.} \label{fig.processes_containers}
    \end{figure}

One strategic difference in our algorithm implementation is the reproduction
process, which is flexible to work in parallel with multiple couple selection
methods, for example, tournament selection, random selection (Closed
Reproduction process), and couple match by creating a new mating individual
(Open Reproduction process). We use many combinations of the containerized
processes, up to the minimum number required to obtain good results.
Figure~\ref{fig.processes_containers} shows a comparison of only two alternatives for the
implementation of the algorithm. Our experimentation started with a
configuration of ten processes and ended in five, shown on the left and right
sides of Fig.~\ref{fig.processes_containers}, respectively.

\subsection{Experiment Configuration}

In our four experiments, we needed to match or balance the experimentation
parameters according to the specifications of the algorithm used by the DEAP
library. This is to be able to verify if our algorithm would also converge on
the solutions in a similar number of evaluations and execution time.
Table~\ref{tab.configuration} shows the OneMax initial configuration for DEAP and Life-Cycle
experiment.

\begin{table}[]
    \centering        
    \caption{OneMax initial configuration for DEAP and Life-Cycle experiment.}\label{tab.configuration}
    \begin{tabular}{|l|l|l|}
    \hline
    \textbf{Configuration} & \textbf{DEAP} & \textbf{Life-Cycle} \\ \hline
    Population & 60 & 60 \\ \hline
    Max Generation & 20 & 20 \\ \hline
    Stagnation & Off & 10 \\ \hline
    Chromosome Length & 20 & 20 \\ \hline
    Target Fitness & 20 & 20 \\ \hline
    Crossover Rate & 100 & 100 \\ \hline
    Mutation Rate & 7 & 7 \\ \hline
    Tournament Rate & 100 & 50 \\ \hline
    Tournament Sample & 3 & 4 \\ \hline
    Open Reproduction Rate & NA & 5 \\ \hline
    Closed Reproduction Rate & NA & 45 \\ \hline
    Max Age & NA & 80 \\ \hline
    Base Approval & NA & 80 \\ \hline
    Goal Approval & NA & 100 \\ \hline
    \end{tabular}
    \end{table}

\subsection{Experiment Results}

For each experiment, we ran 60 independent executions per algorithm and
recorded the following results: Last Generation, Total Evaluations, Time
(seconds), Evaluations/second. The labels used on the results of our summarized
experiments tables are the following:

\begin{itemize}
    \item   Last Gen.   is the generation that found the solution.
    \item   Eval.       is the total number of evaluations the algorithm executed. 
    \item   Time (sec)  is the total elapsed or wall clock time, in seconds. 
    \item   Eval/sec    is the calculated rate of evaluations per second.
\end{itemize}

\subsubsection{Experiment 1} The goal of our first OneMax experiment was to
make sure our Life-Cycle algorithm worked as expected, converging on the
solution. For this experiment, we intentionally used delays (on the tenth of a
second magnitude) to follow the Life-Cycle algorithm behavior on the console
output. For this experiment, we compared the DEAP algorithm versus the
Life-Cycle using ten processes (on containers) where we show the summarized
results in Table~\ref{tab.experiment1}, and Figure~\ref{fig.experiment1} shows
their Box and Whisker chart.

\begin{table}[]
    \centering        
    \caption{Experiment 1 results: OneMax DEAP versus Life-Cycle (10 processes).}\label{tab.experiment1}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{OneMax DEAP} & \multicolumn{4}{l|}{Life-Cycle (10P)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 6.5 & 391 & 0.036 & 10,836 & 9.6 & 578 & 6.830 & 85 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}}
    \caption{Box and whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle.} \label{fig.experiment1}
% You need to label axis y - JJ
  \end{figure}

\subsubsection{Experiment 2} The goal of our second experiment was to confirm
the Life-Cycle algorithm continued working as expected, converging on the
solution. For this experiment, we reduced the time used on delays (now on the
thousands of a second magnitude) to follow the Life-Cycle algorithm behavior.
For this experiment, we only used tournament selection for the reproduction, on
the first configuration running the Life-Cycle on ten processes, versus the
second configuration where we reduced the processes to the minimum basic 5. We
show the summarized results in Table~\ref{tab.experiment2}, and
Figure~\ref{fig.experiment2} shows their Box and Whisker chart.

\begin{table}[]
    \centering        
    \caption{Experiment 2 results, Life-Cycle Tournament selection: 10 versus 5 processes.}\label{tab.experiment2}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{LifeCycle (Tourn. 10P)} & \multicolumn{4}{l|}{LifeCycle (Tourn. 5P)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 7.2 & 434 & 0.740 & 587 & 8.2 & 495 & 0.826 & 599 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig7_experiment02_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 2: Life-Cycle Tournament selection (10 versus 5 processes).} \label{fig.experiment2}
    \end{figure}

\subsubsection{Experiment 3} The goal of our third experiment was to follow and
study the behavior of the Life-Cycle algorithm that continued converging on the
solution. For this experiment, we remained using minimal delays (thousands of a
second magnitude). For this experiment, we only used tournament selection for
the reproduction, on the first configuration running the Life-Cycle on six
processes, two of whom was the Death process, versus the second configuration
where we reduced the processes to the minimum (five) but increasing the (Death)
goal approval range to 115. We show the summarized results in
Table~\ref{tab.experiment3}, and Figure~\ref{fig.experiment3} shows their Box
and Whisker chart.

\begin{table}[]
    \centering        
    \caption{Experiment 3 results, Life-Cycle Tournament: 6 processes (Death x2) versus 5 processes (80 to 115 goal).}\label{tab.experiment3}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{LifeCycle (Tourn. 6P, Death x2)} & \multicolumn{4}{l|}{LifeCycle (Tourn. 5P, 80-115g)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 8.0 & 483 & 0.846 & 571 & 6.4 & 384 & 0.695 & 553 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig8_experiment03_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 3: Life-Cycle Tournament (6 processes double Death, versus 5 processes with an 80 to 115 goal approval).} \label{fig.experiment3}
    \end{figure}

\subsubsection{Experiment 4} The goal of our fourth and last experiment was to
follow and study the behavior of the Life-Cycle algorithm that continued
converging on the solution. For this experiment, we remained using minimal
delays (thousands of a second magnitude). For this experiment, we compared the
OneMax DEAP implementation versus the Life-Cycle algorithm, only using
tournament selection for the reproduction, with the Life-Cycle configuration
running on the minimum (five) processes but increasing the (Death) goal
approval range to 125. We show the summarized results in
Table~\ref{tab.experiment4}, and Figure~\ref{fig.experiment4} shows their Box
and Whisker chart.

\begin{table}[]
    \centering        
    \caption{Experiment 4 results, OneMax DEAP versus Life-Cycle Tournament: 5 processes (80 to 125 goal).}\label{tab.experiment4}
    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
    \hline
    Run & \multicolumn{4}{l|}{OneMax DEAP} & \multicolumn{4}{l|}{Life-Cycle (Tourn. 5P, 80-125g)} \\ \hline
    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
    Avg. & 6.5 & 391 & 0.036 & 10,836 & 6.3 & 377 & 0.678 & 556 \\ \hline
    \end{tabular}
    \end{table}

\begin{figure}
    \fbox{\includegraphics[width=\textwidth]{img/fig9_experiment4_chart.pdf}}
    \caption{Box and Whisker chart for the Experiment 4: OneMax DEAP versus Life-Cycle Tournament (5 processes with an 80 to 125 goal approval).} \label{fig.experiment4}
    \end{figure}

\section{Discussion}
\label{section.discussion}

At some crucial moments during our research, we got the feeling we were doing
nature reverse engineering. One strategy was to let our imagination run wild
and go for the simple solution. One of our earlier experiment's findings was to
find balance, like the yin and yang, between death and reproduction.

In our experiments, we found that when solving simple problems, the cost of
communication between containers can become a factor to increase the total
performance time, even though, we believe that the opposite must also be true.
When solving complex problems, distributing the work on multiple resources
should reduce throughput time, making the communication cost negligible.

We must acknowledge the performance time of the DEAP library
\cite{fortin2012deap} is highly efficient and short, due in part because the
processing work execution is on a single processor with multiple cores, where
the communication time is nearly non-existent. In contrast, our algorithm
implementation requires a minimum of five containers and a message queue
server. Even though the container work has proven to be very effective and
efficient \cite{merelo2016performance,valdez2021container}, we must consider
some time was added to our experiments by the minimal delays (in the thousands
of a second magnitude) we used to keep the process execution relatively random,
to mimic how the life-cycle stages work in nature \cite{read1968system}. As
future work, we could test the Life-Cycle algorithm behavior by eliminating all
remaining delays.

This scheme allows for multiple parameter's fine tuning, granting us the
freedom to experiment with different selection and reproduction strategies
simultaneously, which will impact how fast it finds the solution and the
obtained quality.

\section{Conclusions}
\label{section.conclusions}

We implemented the algorithm with Docker containers by solving the OneMax
problem comparing it with a traditional (sequential) GA algorithm, where it
showed favorable and promising results. To further validate this work, we could
use control or some more complex and demanding problem that requires computing
real numbers \cite{stanley2002evolving,miikkulainen2019evolving}.

As the complexity of problems increases, it is essential to have a scalable,
replicable, and fault-tolerant model that uses collaborative techniques to work
in the cloud, where multiple resources will be communicating asynchronously.
This research has shown that it is possible to evolve a population of
individuals, similar to a Genetic Algorithm (GA), using a distributed,
parallel, and asynchronous methodology.

\begin{acknowledgement}
    This paper has been supported in part by projects DeepBio (TIN2017--85727--C4--2--P) and TecNM Project 11356.21\@.
\end{acknowledgement}

% ---- Bibliography ----
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{bib/bibliografia.bib}

\end{document}

### 2022-09-22 paper.tex
Update Reflow
Update Introduction
Work in progress.

@@
 
-\abstract*{In previous work, we introduced an algorithm inspired by the biological Life Cycle of animal species, consisting of the stages: birth, growth, reproduction, and death.
-As in nature, population individuals grow older and age.
-In this algorithm's reproduction process, couples must match by mutual attraction, where sometimes individuals won't procreate offspring because of the mate's low appeal.
-As time passes, the environment kills its individuals either because of low fitness or age, causing occasional population extinction.
-When this condition presents, it is required to create a new population if evaluations are available and termination conditions are favorable to continue.
-Some alternatives we explored to restart this new population are the random generation of a new set of candidate solutions and the creation of a new set of candidate solutions based on either: a mix of elements from the best historically found candidate solutions set (Elite); the mutation with uniform modification from the Elite or the historically best-found solution (Champion); crossing the Champion with the Elite; the projection of the Elite towards the Champion; based on random use of the previous alternatives.
-In this paper, we present one of the most promising alternatives to solve population extinction caused by nature's pressure in the Life Cycle algorithm: the projection of the Elite towards the Champion, where we compare the results obtained with the latter and the random use of all the alternatives, using classic benchmark functions for optimization for comparison.}
+\abstract*{In previous work, we introduced an algorithm inspired by the
+biological Life Cycle of animal species, consisting of the stages: birth,
+growth, reproduction, and death. As in nature, population individuals grow
+older and age. In this algorithm's reproduction process, couples must match by
+mutual attraction, where sometimes individuals won't procreate offspring
+because of the mate's low appeal. As time passes, the environment kills its
+individuals either because of low fitness or age, causing occasional population
+extinction. When this condition presents, it is required to create a new
+population if evaluations are available and termination conditions are
+favorable to continue. Some alternatives we explored to restart this new
+population are the random generation of a new set of candidate solutions and
+the creation of a new set of candidate solutions based on either: a mix of
+elements from the best historically found candidate solutions set (Elite); the
+mutation with uniform modification from the Elite or the historically
+best-found solution (Champion); crossing the Champion with the Elite; the
+projection of the Elite towards the Champion; based on random use of the
+previous alternatives. In this paper, we present one of the most promising
+alternatives to solve population extinction caused by nature's pressure in the
+Life Cycle algorithm: the projection of the Elite towards the Champion, where
+we compare the results obtained with the latter and the random use of all the
+alternatives, using classic benchmark functions for optimization for
+comparison.}
 
-\abstract{In previous work, we introduced an algorithm inspired by the biological Life Cycle of animal species, consisting of the stages: birth, growth, reproduction, and death.
-As in nature, population individuals grow older and age.
-In this algorithm's reproduction process, couples must match by mutual attraction, where sometimes individuals won't procreate offspring because of the mate's low appeal.
-As time passes, the environment kills its individuals either because of low fitness or age, causing occasional population extinction.
-When this condition presents, it is required to create a new population if evaluations are available and termination conditions are favorable to continue.
-Some alternatives we explored to restart this new population are the random generation of a new set of candidate solutions and the creation of a new set of candidate solutions based on either: a mix of elements from the best historically found candidate solutions set (Elite); the mutation with uniform modification from the Elite or the historically best-found solution (Champion); crossing the Champion with the Elite; the projection of the Elite towards the Champion; based on random use of the previous alternatives.
-In this paper, we present one of the most promising alternatives to solve population extinction caused by nature's pressure in the Life Cycle algorithm: the projection of the Elite towards the Champion, where we compare the results obtained with the latter and the random use of all the alternatives, using classic benchmark functions for optimization for comparison.}
+\abstract{In previous work, we introduced an algorithm inspired by the
+biological Life Cycle of animal species, consisting of the stages: birth,
+growth, reproduction, and death. As in nature, population individuals grow
+older and age. In this algorithm's reproduction process, couples must match by
+mutual attraction, where sometimes individuals won't procreate offspring
+because of the mate's low appeal. As time passes, the environment kills its
+individuals either because of low fitness or age, causing occasional population
+extinction. When this condition presents, it is required to create a new
+population if evaluations are available and termination conditions are
+favorable to continue. Some alternatives we explored to restart this new
+population are the random generation of a new set of candidate solutions and
+the creation of a new set of candidate solutions based on either: a mix of
+elements from the best historically found candidate solutions set (Elite); the
+mutation with uniform modification from the Elite or the historically
+best-found solution (Champion); crossing the Champion with the Elite; the
+projection of the Elite towards the Champion; based on random use of the
+previous alternatives. In this paper, we present one of the most promising
+alternatives to solve population extinction caused by nature's pressure in the
+Life Cycle algorithm: the projection of the Elite towards the Champion, where
+we compare the results obtained with the latter and the random use of all the
+alternatives, using classic benchmark functions for optimization for
+comparison.}
 
@@
 
+\newpage
 \section{Introduction}
@@
 \cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but as
-their complexity increases so does the computing power required
+their complexity increases so does the computing power required to execute them
 \cite{ontiveros2018high}. One strategy to address this processing need is to
 use distributed computing \cite{thain2005distributed}, or the resources
-available in the cloud \cite{garcia2013there,eshratifar2019bottlenet} to help
-find the solution. This strategy gives us elasticity to adjust (increase or
-reduce) the computing power to achieve a balance according to the nature of the
-problem.
+available in the cloud to help find the solution
+\cite{garcia2013there,eshratifar2019bottlenet}. This strategy gives us
+elasticity to increase (or reduce) the computing power to achieve a balance
+according to the nature of the problem.
 
-One of the problems that we have identified in this research is that most
-bio-inspired algorithms are designed with a traditionally sequential
-perspective \cite{porto2018evolutionary,back1996evolutionary}, where each
-process must wait for the previous task to finish before continuing. Some
-architectures address this issue
-\cite{valdez2021container,garcia2015evospace,merelo2016nodio}, what
-distinguishes this proposal is the introduction of  an algorithm designed in its
-entirety as a native solution in the cloud, fully distributed, where its
-processes are executed in parallel and interaction takes place asynchronously. This technique makes it
+Most bio-inspired algorithms are traditionally designed with a sequential
+(synchronous) perspective \cite{porto2018evolutionary,back1996evolutionary},
+where each process must wait for the previous task to finish before continuing.
+Our proposal presents an algorithm in its entirety as a native solution in the
+cloud, fully distributed, where its processes are executed in parallel and
+asynchronously. We designed the algorithm as a cloud-native solution using the
+cloud available resources to divide the processing workload, among several
+computers or running the algorithm as a cloud service. This technique makes it
 easy to scale the computing power according to the complexity required by the
@@
 
-We designed our algorithm using observation, analysis, and abstraction in
-nature to identify what most species in the animal kingdom have in common,
-where individuals of a population that best adapt to the environment have
-greater chances of survival, reproduction, and improvement of the species.
-Imagining as if the task of writing these rules of evolution was in our hands,
-questioning how we could solve it?
+In previous work, we introduced an algorithm inspired by the biological
+life-cycle of animal species. As in nature, population individuals grow older
+and age. In this algorithm's reproduction process, couples must match by mutual
+attraction, where sometimes individuals won't procreate offspring because of
+the mate's low appeal. As time passes, the environment kills its individuals
+either because of low fitness or age, causing occasional population extinction.
+When this condition presents itself, it is required to create a new population
+to continue evolution (restart). We previously used to generate a new random
+set of solutions, with the cost of losing all evolution knowledge.
 
-Like nature, we identified what most species have in common in the life cycle.
-Our algorithm works on a constantly evolving population, experiencing the
-stages that all living beings undergo \cite{read1968system}: being born,
-growing up, reproducing, and dying, where each of these stages will be
-processes (of our algorithm) that randomly affect the population individuals,
-emulating the organic way.
-
-The main contribution of the paper is to design and create a new algorithm with
-the purpose to demonstrate that it is possible to evolve a population of
-individuals, similar to a Genetic Algorithm (GA), using a distributed,
-parallel, and asynchronous methodology by implementation and testing of the
-algorithm.
+The main contribution of this paper is to demonstrate that it is possible to
+evolve a population of individuals, similar to a Genetic Algorithm (GA), using
+a distributed, parallel, and asynchronous methodology by the algorithm
+implementation and testing. We improve the algorithm behaviour by solving
+population extinction caused by nature's pressure in the Animal Life Cycle
+Algorithm with one of the most promising alternatives: the projection of the
+Elite towards the Champion, where we compare the results obtained with the
+latter and the random use of the more traditional alternatives (mutation and
+crossover), using classic benchmark functions for optimization for comparison.
 
 We present the description of the following sections in our paper. First, we
-introduce our algorithm inspired by the Life-Cycle of animal species in
-% Please use capitalization consistently; I don't think this should go in Caps - JJ
+illustrate our algorithm model, the problem found with the occasional
+population extinction and our proposed solution in
 section~\ref{section.proposal}, followed by our experimental configuration and
-results in section~\ref{section.experiments}, we analyze and describe some of
-our research findings in section~\ref{section.discussion}, and we finalize by
-presenting some inferences based on our experiments' results in
+results in section~\ref{section.experiments}, where we continue to analyze and
+describe some of our research findings in section~\ref{section.discussion}. We
+finalize by presenting some inferences based on our experiments results in
 section~\ref{section.conclusions}.
+
+%PREVIOUSLY / FROM THE FIRST CHAPTER
+%We designed our algorithm using observation, analysis, and abstraction in nature to identify what most species in the animal kingdom have in common, where individuals of a population that best adapt to the environment have greater chances of survival, reproduction, and improvement of the species.
+Imagining as if the task of writing these rules of evolution was in our hands, questioning how we could solve it?
+%Like nature, we identified what most species have in common in the life cycle.
+Our algorithm works on a constantly evolving population, experiencing the stages that all living beings undergo \cite{read1968system}: being born, growing up, reproducing, and dying, where each of these stages will be processes (of our algorithm) that randomly affect the population individuals, emulating the organic way.
 

### 2022-09-23 paper.tex
Updated Proposal
Work in progress. Starting with Section 3 Experiments

@@
 
-%PREVIOUSLY / FROM THE FIRST CHAPTER
-%We designed our algorithm using observation, analysis, and abstraction in nature to identify what most species in the animal kingdom have in common, where individuals of a population that best adapt to the environment have greater chances of survival, reproduction, and improvement of the species.
-Imagining as if the task of writing these rules of evolution was in our hands, questioning how we could solve it?
-%Like nature, we identified what most species have in common in the life cycle.
-Our algorithm works on a constantly evolving population, experiencing the stages that all living beings undergo \cite{read1968system}: being born, growing up, reproducing, and dying, where each of these stages will be processes (of our algorithm) that randomly affect the population individuals, emulating the organic way.
-
 \section{Proposal}
@@
 
-Many of the publications with the most influence on our research
-~\cite{valdez2021container,garcia2021event,merelo2016performance,merelo2016nodio}
-propose a cloud-native optimization architecture that features population-based
-algorithms. They present ideas such as those mentioned in Figure~\ref{fig.background},
-which planted the seed of thought of our current paper.
+Our inspiration for this algorithm was found on the study and observation of
+nature, using general abstraction to identify what most animal species have in
+common: the life cycle. We present an algorithm inspired by the biological
+life-cycle of animal species, which consists of several stages
+\cite{read1968system}: birth, growth, reproduction, and death. The combination
+of those processes results in evolution. As in nature, we intend to execute all
+these stages in parallel and asynchronously on a constantly evolving
+population.
+
+\subsection{Algorithm Model}
+
+This algorithm seeks to imitate the natural life cycle, where new individuals
+are born at any moment and mature over time, where they age and then suffer
+mutations throughout their lives. In reproduction, couples match by mutual
+attraction. Death can happen to everyone: from a newborn to an aged adult,
+where the individual's fitness will impact their longevity. We display the
+general model concept in Figure~\ref{fig.algorithm_model}.
+
+\subsubsection{Birth} Birth is the first process of our algorithm, and it is
+responsible for the initial generation of individuals. This algorithm starts
+with a randomly generated population.
+
+\subsubsection{Growth} As in nature, all individuals constantly grow, mature,
+or age. With increasing age, individuals may lose strength but may also gain
+knowledge to solve problems. We represent this with a possible mutation in each
+increment of age.
+
+\subsubsection{Reproduction} This process will select random pairs of
+individuals to evaluate their attraction as a couple, where this attraction
+will depend on fitness. The better individual's fitness, the more attractive it
+will be. Not all couples will be compatible, so reproduction will not always be
+possible. When the breeding is successful, a new pair of individuals will be
+born (offspring).
+
+\subsubsection{Death} The death stage represents the challenges and adversities
+that life presents. This process evaluates the individual resistance to survive
+in the environment. The better fitness the individual has will increase its
+chances of survival. As time progresses, the demands of nature will also
+increase, pushing for only the best individuals to survive.
 
@@
     \centering
-    \includegraphics[width=80mm]{img/fig1_background.pdf}
-    \caption{These ideas planted the seed of thought in our algorithm proposal.} \label{fig.background}
+    \includegraphics[width=80mm]{img/fig_algorithm_model.pdf}
+    \caption{Animal Life Cycle Algorithm model.} \label{fig.algorithm_model}
     \end{figure}
 
-Our main inspiration for this algorithm was born from the study and observation
-of nature, where many successful optimization algorithms have previously found
-their own. Our focus was not on a single animal species but all of them, using
-general abstraction to identify what those species have in common.
+\subsection{Problem}
 
-Some questions in our train of thought were: How does nature work? Is evolution
-real? How do we enforce natural selection in evolution? What is the role of the
-attraction between couples on reproduction? How much of a factor is the
-attraction's role in the evolution of the species? What is the role of death in
-all of this? How much of an impact does death have on the evolution of a
-species? How do we include those ideas into our algorithm?
+In this algorithm's reproduction process, we find mating couples by mutual
+attraction, where sometimes individuals won't procreate offspring because of
+the mate's low appeal. As time passes, the environment could kill its
+individuals either because they have low fitness or age, leading to extinction,
+meaning there are no more individuals in the population left to reproduce. When
+this condition presents, if evaluations are available and termination
+conditions enable the algorithm to continue the search, it is required to
+create a new set of individuals. We illustrate the general flowchart for the
+Life-Cycle algorithm in Figure~\ref{fig.flowchart}.
 
-In our analysis, we consider a broad animal spectrum, from bacteria to humans
-and lions, finding our inspiration on the biological Life Cycle of the animal
-species, which consists of several stages \cite{read1968system}: birth, growth,
-reproduction, and death. As in nature, we intend to execute all these stages in
-parallel and asynchronously on a population that evolves constantly. The
-combination of those processes is what we call evolution.
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig_flowchart.pdf}
+    \caption{Animal Life-Cycle Algorithm general flowchart.} \label{fig.flowchart}
+    \end{figure}
 
-One of the main challenges when designing the algorithm was how to capture the
-essence of life by reflecting a population evolution?. In our minds, it was
-clear this task requires a combination of simultaneous working forces that
-influences the population improvement over time. Our strategy was simple:
-divide and conquer, looking into the clouds. Enter cloud-computing: previous
-cloud-computing algorithms have proven successful results working in
-optimization problems \cite{valdez2021container,garcia2021event}.
+\subsection{Proposed Solution}
 
-We turned back to our genetic algorithms knowledge, mixed with our inspiration
-and cloud computing, and designed the algorithm with the quest to divide the
-processing workload among multiple computers. This strategy would also make it
-possible to run our algorithm as a cloud service. Theoretically, one
-consequence of the workload distribution is to obtain lower execution times.
+In this article, we test various strategies to generate a new population to
+replace individuals that have already died (or were discarded) due to their
+aptitude, as happens in the life cycle. We previously used to generate a new
+random set of solutions, with the cost of losing all evolution knowledge. The
+strategy we describe on this paper uses elites to take advantage of the
+historical evolution, especially the best individuals, where we look for the
+offspring of the elite set to be somewhat close to them. We use the golden
+ratio to compute the distance between new individuals in the population, making
+an improved distribution.
 
-This algorithm seeks to imitate the natural life cycle, where new individuals
-are born at any moment and mature over time, where they age and suffer
-mutations throughout their lives. In reproduction, couples match by mutual
-attraction, and they may have offspring. Death can happen to everyone: from a
-newborn to an aged adult, where the individual's fitness will impact their
-longevity. The general model concept is shown in Figure~\ref{fig.proposal}. The general
-flowchart for the Life-Cycle algorithm is described in Figure~\ref{fig.flowchart}.
+We propose one promising alternative to restart the population, to solve
+extinction caused by nature's pressure in the Life Cycle algorithm: the
+projection of the historically best-found candidate solutions (Elite) towards
+the best-found candidate solution (Champion). This article proposes some
+strategies to carry out this operation, where the presented distribution
+strategy obtained best results.
+
+\subsubsection{How does it work?} Based on the historically best candidate
+solution and the elite set, we use the Golden Ratio (shown in
+Figure~\ref{fig.golden_ratio}) to compute the distance between new individuals
+in the population, making an improved distribution. It randomly selects a
+solution from the elite set and uses the Golden Ratio to compute multiple
+solutions against the best found candidate.
 
@@
     \centering
-    \includegraphics[width=70mm]{img/fig2_proposal.pdf}
-    \caption{Algorithm model inspired by the animal species' biological Life-Cycle.} \label{fig.proposal}
+    \includegraphics[width=25mm]{img/fig_golden_ratio.pdf}
+    \caption{Golden Ratio equation.} \label{fig.golden_ratio}
     \end{figure}
 
-\begin{figure}
-    \includegraphics[width=\textwidth]{img/fig4_flowchart.pdf}
-    \caption{Life-Cycle algorithm general flowchart.} \label{fig.flowchart}
-% Several terms are introduced here that are not defined in the text, like "champion list" and "attraction" - JJ
-    \end{figure}
-
-\subsection{Birth}
-
-This algorithm starts with a randomly generated population, where the processes
-will interact with the population independently. This means that at any given
-time, any individual can experience any of these processes. Birth is the first
-process of our algorithm, and it is responsible for the initial generation of
-individuals.
-
-\subsection{Growth}
-
-As in nature, all individuals constantly grow, mature, or age. With increasing
-age, individuals may lose strength but also gain more knowledge to solve
-problems. We represent this with a possible mutation in each increment of age.
-The growth process will take an individual to assess whether it's ready to
-mature and undergo changes. % Not learning?  JJ
-
-\subsection{Reproduction}
-
-The attraction of a couple will depend on fitness: the better individual's
-fitness, the more attractive it will be, making it easier to find mating
-matches. This process will be taking random pairs of individuals to evaluate
-their attraction as a couple, to try to breed; when the gestation is
-successful, a new pair of individuals will be born (as the offspring). Not all
-couples will be compatible, so reproduction will not always be possible, but
-the problem arises: how to quantify the attraction between two individuals?
-
-We could have used several strategies to evaluate this attraction. Considering
-this algorithm takes a similar focus as the study of bacteria growth in
-microbiology, where we can observe and analyze the evolution of a population
-over time. As in nature' most species, the bigger a specimen is, the more
-attractive it is to its mating candidates. To be consistent with both ideas in
-% Er... not really. It depends on health, mainly - JJ
-our algorithm, we use the equation of Newton's Law of Universal Gravitation (1)
-to calculate the attraction between two individuals, where we visualize the
-individual fitness as its mass when using the equation. In previous work,
-Newton's Law of Universal Gravitation has shown success in helping to solve
-optimization problems \cite{sanchez2014fuzzy,rashedi2009gsa}.
+This strategy is how we can calculate the projection of the historically
+best-found candidate solutions (Elite) towards the best-found candidate
+solution (Champion). To illustrate this concept we use
+Figure~\ref{fig.elite_projection}, placing the Elite solution on the far right
+and the Champion solution on the left corner, where a higher number of new
+solutions will be closer to the Champion.
 
@@
     \centering
-    \includegraphics[width=50mm]{img/fig3_newtonslaw.pdf}
-    \caption{Newton's Law of Universal Gravitation.} \label{fig.newtonslaw}
+    \includegraphics[width=0.65\textwidth]{img/fig_elite_projection.pdf}
+    \caption{Projection of the historically Elite solutions towards the Champion.} \label{fig.elite_projection}
     \end{figure}
 
-Where:
-\begin{itemize}
-    \item[]	    F is the gravitational force acting between two objects.
-    \item[]	    m1 and m2 are the masses of the objects.
-    \item[]	    r is the distance between the centers of their masses.
-    \item[]	    G is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2.
-\end{itemize}
+This process generates new solutions that will be the new population set. It
+uses the Golden Ratio to progressively aproximate from an Elite solution
+towards the Champion. This strategy facilitates to find apparently hidden
+solutions, having an exploitation emphasis.
+Figure~\ref{fig.elite_projection_swarm} displays the projection of five Elite
+solutions (on the corners) towards the Champion (on the center).
 
-% to be honest, I find this a bit far fetched. How do you define mass? is it related to fitness? - JJ
-
-\subsection{Death}
-
-The death stage represents the challenges and adversities that life presents to
-overcome. This process evaluates the individual resistance to survive in the
-environment. The better fitness the individual has will increase its chances of
-survival. As time progresses, the demands of nature will also increase, pushing
-for only the best individuals to survive.
+\begin{figure}
+    \centering
+    \includegraphics[width=0.85\textwidth]{img/fig_elite_projection_swarm.pdf}
+    \caption{Projection of five Elite solutions towards the Champion, results in a mini-swarm.} \label{fig.elite_projection_swarm}
+    \end{figure}
 
@@
 \label{section.experiments}
+
+ALTO / HASTA AQUI VAMOS.
+
+%----------------------------------------------------
+%----------------------------------------------------
+%PREVIOUSLY / FROM THE FIRST CHAPTER
+%We designed our algorithm using observation, analysis, and abstraction in nature to identify what most species in the animal kingdom have in common, where individuals of a population that best adapt to the environment have greater chances of survival, reproduction, and improvement of the species.
+Imagining as if the task of writing these rules of evolution was in our hands, questioning how we could solve it?
+%Like nature, we identified what most species have in common in the life cycle.
+Our algorithm works on a constantly evolving population, experiencing the stages that all living beings undergo \cite{read1968system}: being born, growing up, reproducing, and dying, where each of these stages will be processes (of our algorithm) that randomly affect the population individuals, emulating the organic way.
+%Many of the publications with the most influence on our research ~\cite{valdez2021container,garcia2021event,merelo2016performance,merelo2016nodio} propose a cloud-native optimization architecture that features population-based algorithms.
+They present ideas such as those mentioned in Figure~\ref{fig.background}, which planted the seed of thought of our current paper.
+%Some questions in our train of thought were: How does nature work?
+Is evolution real?
+How do we enforce natural selection in evolution?
+What is the role of the attraction between couples on reproduction?
+How much of a factor is the attraction's role in the evolution of the species?
+What is the role of death in all of this?
+How much of an impact does death have on the evolution of a species?
+How do we include those ideas into our algorithm?
+%One of the main challenges when designing the algorithm was how to capture the essence of life by reflecting a population evolution?.
+In our minds, it was clear this task requires a combination of simultaneous working forces that influences the population improvement over time.
+Our strategy was simple: divide and conquer, looking into the clouds.
+Enter cloud-computing: previous cloud-computing algorithms have proven successful results working in optimization problems \cite{valdez2021container,garcia2021event}.
+%We turned back to our genetic algorithms knowledge, mixed with our inspiration and cloud computing, and designed the algorithm with the quest to divide the processing workload among multiple computers.
+This strategy would also make it possible to run our algorithm as a cloud service.
+Theoretically, one consequence of the workload distribution is to obtain lower execution times.
+%----------------------------------------------------
+%Birth: This algorithm starts with a randomly generated population, where the processes will interact with the population independently.
+This means that at any given time, any individual can experience any of these processes.
+Birth is the first process of our algorithm, and it is responsible for the initial generation of individuals.
+%Growth: As in nature, all individuals constantly grow, mature, or age.
+With increasing age, individuals may lose strength but also gain more knowledge to solve problems.
+We represent this with a possible mutation in each increment of age.
+The growth process will take an individual to assess whether it's ready to mature and undergo changes.
+%Reproduction: The attraction of a couple will depend on fitness: the better individual's fitness, the more attractive it will be, making it easier to find mating matches.
+This process will be taking random pairs of individuals to evaluate their attraction as a couple, to try to breed; when the gestation is successful, a new pair of individuals will be born (as the offspring).
+Not all couples will be compatible, so reproduction will not always be possible, but the problem arises: how to quantify the attraction between two individuals?
+%------------- We could have used several strategies to evaluate this attraction.
+Considering this algorithm takes a similar focus as the study of bacteria growth in microbiology, where we can observe and analyze the evolution of a population over time.
+As in nature' most species, the bigger a specimen is, the more attractive it is to its mating candidates.
+To be consistent with both ideas in our algorithm, we use the equation of Newton's Law of Universal Gravitation (1) to calculate the attraction between two individuals, where we visualize the individual fitness as its mass when using the equation.
+In previous work, Newton's Law of Universal Gravitation has shown success in helping to solve optimization problems \cite{sanchez2014fuzzy,rashedi2009gsa}.
+%Death: The death stage represents the challenges and adversities that life presents to overcome.
+This process evaluates the individual resistance to survive in the environment.
+The better fitness the individual has will increase its chances of survival.
+As time progresses, the demands of nature will also increase, pushing for only the best individuals to survive.
+%----------------------------------------------------
+
+\section{Another Section}
+\label{section.another_section}
 
@@
     \item   Eval/sec    is the calculated rate of evaluations per second.
+\end{itemize}
+
+Where:
+\begin{itemize}
+    \item[]	    F is the gravitational force acting between two objects.
+    \item[]	    m1 and m2 are the masses of the objects.
+    \item[]	    r is the distance between the centers of their masses.
+    \item[]	    G is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2.
 \end{itemize}

### 2022-09-23 paper.tex
Updated Improvements
Work in progress.

@@
 evolve a population of individuals, similar to a Genetic Algorithm (GA), using
-a distributed, parallel, and asynchronous methodology by the algorithm
-implementation and testing. We improve the algorithm behaviour by solving
+a distributed, parallel, and asynchronous methodology by algorithm
+implementation and testing. We improve the algorithm behavior by solving
 population extinction caused by nature's pressure in the Animal Life Cycle
@@
 We present the description of the following sections in our paper. First, we
-illustrate our algorithm model, the problem found with the occasional
-population extinction and our proposed solution in
+illustrate our algorithm model, the encountered problem with the occasional
+population extinction, and our proposed solution in
 section~\ref{section.proposal}, followed by our experimental configuration and
@@
 describe some of our research findings in section~\ref{section.discussion}. We
-finalize by presenting some inferences based on our experiments results in
-section~\ref{section.conclusions}.
+finalize by presenting some inferences based on the results of our experiments
+in section~\ref{section.conclusions}.
 
@@
 
-Our inspiration for this algorithm was found on the study and observation of
+Our inspiration for this algorithm was found in the study and observation of
 nature, using general abstraction to identify what most animal species have in
@@
 random set of solutions, with the cost of losing all evolution knowledge. The
-strategy we describe on this paper uses elites to take advantage of the
+strategy we describe in this paper uses elites to take advantage of the
 historical evolution, especially the best individuals, where we look for the
@@
 strategies to carry out this operation, where the presented distribution
-strategy obtained best results.
+strategy obtained the best results.
 
@@
 solution from the elite set and uses the Golden Ratio to compute multiple
-solutions against the best found candidate.
+solutions against the best-found candidate.
 
@@
 best-found candidate solutions (Elite) towards the best-found candidate
-solution (Champion). To illustrate this concept we use
+solution (Champion). To illustrate this concept we include
 Figure~\ref{fig.elite_projection}, placing the Elite solution on the far right
@@
 This process generates new solutions that will be the new population set. It
-uses the Golden Ratio to progressively aproximate from an Elite solution
-towards the Champion. This strategy facilitates to find apparently hidden
-solutions, having an exploitation emphasis.
-Figure~\ref{fig.elite_projection_swarm} displays the projection of five Elite
-solutions (on the corners) towards the Champion (on the center).
+uses the Golden Ratio to progressively approximate from an Elite solution to
+the Champion. This strategy facilitates to find apparently hidden solutions,
+having an exploitation emphasis. Figure~\ref{fig.elite_projection_swarm}
+displays the projection of five Elite solutions (on the corners) towards the
+Champion (in the center).
 
@@
 
-ALTO / HASTA AQUI VAMOS.
+As a proof-of-concept, we implemented the algorithm with Docker containers,
+where we compare the results obtained with the projection of the Elite towards
+the Champion strategy and the random use of the more traditional alternatives
+(such as mutation and crossover), using classic benchmark functions for
+optimization as implemented by the DEAP (Distributed Evolutionary Algorithms in
+Python) library \cite{fortin2012deap}.
+
+\subsection{Experimental Setup}
+
+The alternatives to restart this new population are the creation of a new set
+of candidate solutions based on either: The mutation with uniform modification
+from the Elite or the historically best-found solution (Champion); Crossing the
+Champion with the Elite; The projection of the Elite towards the Champion;
+Based on random use of the previous alternatives.
+
+\subsection{ALTO / HASTA AQUI VAMOS}
 

### 2022-09-23 paper.tex
Updated Experimental Setup
Work in progress.

@@
 \usepackage{newtxmath}       % selects Times Roman as basic font
+
+\usepackage{booktabs}       %Booktabs Table Style
 
@@
 
-\subsection{Experimental Setup}
-
 The alternatives to restart this new population are the creation of a new set
@@
 Based on random use of the previous alternatives.
+
+\subsection{Experimental Setup}
+
+The following tables show the configuration used to execute the experiments for
+the analysis and comparison in this paper. In
+Table~\ref{tab.general_configuration}, we can find the General Configuration
+for the Animal Life Cycle Algorithm. All values from this configuration
+remained constant during all phases of the experiment runs. The following
+table, Table~\ref{tab.benchmark_fun_config}, shows the values used for the
+Classic Benchmark Functions for Optimization, where these are adjusted
+accordingly for each function.
+
+% Please add the following required packages to your document preamble:
+% \usepackage{booktabs}
+% To change the size of the font use \scriptsize or \tiny
+\begin{table}[]
+    \scriptsize
+    \centering        
+    \caption{Animal Life Cycle Algorithm (ALCA) General Configuration.}\label{tab.general_configuration}
+    \begin{tabular}{@{}ll@{}}
+    \toprule
+    \multicolumn{2}{l}{ALCA General Configuration} \\ \midrule
+    Function name & ALL \\
+    Population & 500 \\
+    Target error & 1.00E-08 \\
+    Crossover rate & 100 \\
+    Mutation rate & 7 \\
+    Max age & 40 \\
+    Tournament rep. & 100 \\
+    Sample size & 20 \\
+    Base approval & 80 \\
+    Goal approval & 200 \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
+\begin{table}[]
+    \scriptsize
+    \centering        
+    \caption{Classic Benchmark Functions for Optimization Configuration.}\label{tab.benchmark_fun_config}
+    \begin{tabular}{@{}llllllll@{}}
+    \toprule
+    \multicolumn{8}{l}{Benchmark Configuration Setup} \\ \midrule
+    Function name & Ackley & Bohachevsky & Griewank & Rastrigin & Sphere & Rosenbrock & Rosenbrock \\
+    Dimensions & 5, 10 & 5, 10 & 5, 10 & 5, 10 & 5, 10 & 5 & 10 \\
+    Max evaluations & 200,000 & 200,000 & 200,000 & 200,000 & 200,000 & 500,000 & 1,000,000 \\
+    Max stagnation & 50,000 & 50,000 & 50,000 & 50,000 & 50,000 & 125,000 & 250,000 \\
+    Target fitness & -20.0 & -12.0 & -150.0 & -80.0 & -50.0 & -3500.0 & -3500.0 \\
+    Bound matrix & {[}-32, 32{]} & {[}-2, 2{]} & {[}-500, 500{]} & {[}-5, 5{]} & {[}-5, 5{]} & {[}-2, 2{]} & {[}-2, 2{]} \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
+\subsection{Experiment Results}
+
+For each experiment, we ran 60 independent executions per algorithm and
+recorded the following results: Last Generation, Total Evaluations, Time
+(seconds), Evaluations/second. The labels used on the results of our summarized
+experiments tables are the following:
+
+\begin{itemize}
+    \item   Last Gen.   is the generation that found the solution.
+    \item   Eval.       is the total number of evaluations the algorithm executed. 
+    \item   Time (sec)  is the total elapsed or wall clock time, in seconds. 
+    \item   Eval/sec    is the calculated rate of evaluations per second.
+\end{itemize}
 
@@
 %----------------------------------------------------
+%One strategic difference in our algorithm implementation is the reproduction process, which is flexible to work in parallel with multiple couple selection methods, for example, tournament selection, random selection (Closed Reproduction process), and couple match by creating a new mating individual (Open Reproduction process).
+We use many combinations of the containerized processes, up to the minimum number required to obtain good results.
+Figure~\ref{fig.processes_containers} shows a comparison of only two alternatives for the implementation of the algorithm.
+Our experimentation started with a configuration of ten processes and ended in five, shown on the left and right sides of Fig.~\ref{fig.processes_containers}, respectively.
+%In our four experiments, we needed to match or balance the experimentation parameters according to the specifications of the algorithm used by the DEAP library.
+This is to be able to verify if our algorithm would also converge on the solutions in a similar number of evaluations and execution time.
+Table~\ref{tab.configuration} shows the OneMax initial configuration for DEAP and Life-Cycle experiment.
+%----------------------------------------------------
 
@@
 
-As a proof-of-concept, we implemented the algorithm with Docker containers by
-solving the OneMax problem to compare it with a traditional GA algorithm using
-the DEAP (Distributed Evolutionary Algorithms in Python) library
-\cite{fortin2012deap}. The OneMax problem \cite{krejca2020lower,witt2019upper}
-uses a genetic algorithm to evolve a population of randomly generated
-individuals with zeros and ones, and it stops until a solution of only ones is
-found.
-
-\subsection{Experimental Setup}
-
-\begin{figure}
-    \includegraphics[width=\textwidth]{img/fig5_processes_containers.pdf}
-    \caption{Life-Cycle algorithm processes in containers comparison.} \label{fig.processes_containers}
-    \end{figure}
-
-One strategic difference in our algorithm implementation is the reproduction
-process, which is flexible to work in parallel with multiple couple selection
-methods, for example, tournament selection, random selection (Closed
-Reproduction process), and couple match by creating a new mating individual
-(Open Reproduction process). We use many combinations of the containerized
-processes, up to the minimum number required to obtain good results.
-Figure~\ref{fig.processes_containers} shows a comparison of only two alternatives for the
-implementation of the algorithm. Our experimentation started with a
-configuration of ten processes and ended in five, shown on the left and right
-sides of Fig.~\ref{fig.processes_containers}, respectively.
-
 \subsection{Experiment Configuration}
-
-In our four experiments, we needed to match or balance the experimentation
-parameters according to the specifications of the algorithm used by the DEAP
-library. This is to be able to verify if our algorithm would also converge on
-the solutions in a similar number of evaluations and execution time.
-Table~\ref{tab.configuration} shows the OneMax initial configuration for DEAP and Life-Cycle
-experiment.
-
-\begin{table}[]
-    \centering        
-    \caption{OneMax initial configuration for DEAP and Life-Cycle experiment.}\label{tab.configuration}
-    \begin{tabular}{|l|l|l|}
-    \hline
-    \textbf{Configuration} & \textbf{DEAP} & \textbf{Life-Cycle} \\ \hline
-    Population & 60 & 60 \\ \hline
-    Max Generation & 20 & 20 \\ \hline
-    Stagnation & Off & 10 \\ \hline
-    Chromosome Length & 20 & 20 \\ \hline
-    Target Fitness & 20 & 20 \\ \hline
-    Crossover Rate & 100 & 100 \\ \hline
-    Mutation Rate & 7 & 7 \\ \hline
-    Tournament Rate & 100 & 50 \\ \hline
-    Tournament Sample & 3 & 4 \\ \hline
-    Open Reproduction Rate & NA & 5 \\ \hline
-    Closed Reproduction Rate & NA & 45 \\ \hline
-    Max Age & NA & 80 \\ \hline
-    Base Approval & NA & 80 \\ \hline
-    Goal Approval & NA & 100 \\ \hline
-    \end{tabular}
-    \end{table}
 
@@
     \item   Eval/sec    is the calculated rate of evaluations per second.
-\end{itemize}
-
-Where:
-\begin{itemize}
-    \item[]	    F is the gravitational force acting between two objects.
-    \item[]	    m1 and m2 are the masses of the objects.
-    \item[]	    r is the distance between the centers of their masses.
-    \item[]	    G is the gravitational constant: 6.67430(15)×10−11 m3⋅kg−1⋅s−2.
 \end{itemize}

### 2022-09-23 paper.tex
Updated Exeriments
Work in progress.

@@
 
-The alternatives to restart this new population are the creation of a new set
-of candidate solutions based on either: The mutation with uniform modification
-from the Elite or the historically best-found solution (Champion); Crossing the
-Champion with the Elite; The projection of the Elite towards the Champion;
-Based on random use of the previous alternatives.
-
 \subsection{Experimental Setup}
@@
     \toprule
-    \multicolumn{2}{l}{ALCA General Configuration} \\ \midrule
+    \multicolumn{2}{l}{\textbf{ALCA General Configuration}} \\ \midrule
     Function name & ALL \\
@@
     \toprule
-    \multicolumn{8}{l}{Benchmark Configuration Setup} \\ \midrule
+    \multicolumn{8}{l}{\textbf{Benchmark Configuration Setup}} \\ \midrule
     Function name & Ackley & Bohachevsky & Griewank & Rastrigin & Sphere & Rosenbrock & Rosenbrock \\
@@
 
-For each experiment, we ran 60 independent executions per algorithm and
-recorded the following results: Last Generation, Total Evaluations, Time
-(seconds), Evaluations/second. The labels used on the results of our summarized
-experiments tables are the following:
+For each experiment, we ran 30 independent executions per algorithm and
+dimensions specified. We recorded the following results: best found error,
+standard deviation, total number of evaluations, and total elapsed time (in
+seconds). The labels used on the results of our summarized experiments tables
+are the following:
 
 \begin{itemize}
-    \item   Last Gen.   is the generation that found the solution.
-    \item   Eval.       is the total number of evaluations the algorithm executed. 
-    \item   Time (sec)  is the total elapsed or wall clock time, in seconds. 
-    \item   Eval/sec    is the calculated rate of evaluations per second.
+    \item   Error:       is the best found error (or best solution).
+    \item   St-Dev:      is the standard deviation calculated from the error. 
+    \item   Evals.:      is the total number of evaluations the algorithm executed.
+    \item   Time:        is the total elapsed or wall clock time, in seconds. 
 \end{itemize}
+
+The alternatives to restart this new population are the creation of a new set
+of candidate solutions based on either: 1. Crossing the Champion with the Elite;
+2. The mutation with uniform modification from the Elite; 3. The
+projection of the Elite towards the Champion; 4. Based on random use of the
+previous alternatives. We compared three strategies by grouping the previous
+alternatives in the following:
+
+\begin{itemize}
+    \item   Xover Mutation:      Crossing the Champion with the Elite, and the mutation with uniform modification from the Elite.
+    \item   Elite Projection:    The projection of the Elite towards the Champion. 
+    \item   All Random:          Based on random use of the previous alternatives.
+\end{itemize}
+
+\subsubsection{Ackley Benchmark Function Experiment}
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig_fun_ackley.pdf}
+    \caption{Box and whisker chart for the Ackley Benchmark Function, 5 vs 10 Dimensions comparison.} \label{fig.fun_ackley}
+    \end{figure}
+
+\begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Ackley Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.benchmark_fun_ackley5}
+    \begin{tabular}{@{}lllll@{}}
+    \toprule
+    \multicolumn{5}{l}{\textbf{Ackley Function - 5 Dimensions}} \\ \midrule
+     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
+    \textbf{Xover Mutation} & 8.69E-08 & 1.36E-08 & 46,331 & 49.9 \\
+    \textbf{Elite Projection} & 6.33E-08 & 2.70E-08 & 13,811 & 18.1 \\
+    \textbf{All Random} & 6.78E-08 & 2.55E-08 & 30,236 & 32.8 \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
+\begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Ackley Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.benchmark_fun_ackley10}
+    \begin{tabular}{@{}lllll@{}}
+    \toprule
+    \multicolumn{5}{l}{\textbf{Ackley Function - 10 Dimensions}} \\ \midrule
+     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
+    \textbf{Xover Mutation} & 9.35E-08 & 5.93E-09 & 104,842 & 111.7 \\
+    \textbf{Elite Projection} & 5.11E-08 & 3.13E-08 & 16,019 & 20.1 \\
+    \textbf{All Random} & 6.89E-08 & 2.75E-08 & 43,631 & 46.3 \\ \bottomrule
+    \end{tabular}
+    \end{table}
 

### 2022-09-23 paper.tex
Experiment Results Update
Work in progress.

@@
     \includegraphics[width=\textwidth]{img/fig_fun_ackley.pdf}
-    \caption{Box and whisker chart for the Ackley Benchmark Function, 5 vs 10 Dimensions comparison.} \label{fig.fun_ackley}
+    \caption{Box and whisker chart for the Ackley Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_ackley}
     \end{figure}
@@
     \centering
-    \caption{Ackley Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.benchmark_fun_ackley5}
+    \caption{Ackley Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_ackley5}
     \begin{tabular}{@{}lllll@{}}
@@
     \centering
-    \caption{Ackley Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.benchmark_fun_ackley10}
+    \caption{Ackley Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_ackley10}
     \begin{tabular}{@{}lllll@{}}
@@
 
+\subsubsection{Bohachevsky Benchmark Function Experiment}
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig_fun_bohachevsky.pdf}
+    \caption{Box and whisker chart for the Bohachevsky Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_bohachevsky}
+    \end{figure}
+
+\begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Bohachevsky Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_bohachevsky5}
+    \begin{tabular}{@{}lllll@{}}
+    \toprule
+    \multicolumn{5}{l}{\textbf{Function Bohachevsky - 5 Dimensions}} \\ \midrule
+     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
+    \textbf{Xover Mutation} & 7.28E-08 & 2.20E-08 & 15,010 & 24.2 \\
+    \textbf{Elite Projection} & 4.51E-08 & 2.94E-08 & 8,266 & 12.6 \\
+    \textbf{All Random} & 6.16E-08 & 2.85E-08 & 11,998 & 21.7 \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
+\begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Bohachevsky Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_bohachevsky10}
+    \begin{tabular}{@{}lllll@{}}
+    \toprule
+    \multicolumn{5}{l}{\textbf{Function Bohachevsky - 10   Dimensions}} \\ \midrule
+     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
+    \textbf{Xover Mutation} & 8.66E-08 & 1.38E-08 & 40,166 & 44.4 \\
+    \textbf{Elite Projection} & 3.80E-08 & 3.34E-08 & 8,506 & 12.9 \\
+    \textbf{All Random} & 5.34E-08 & 3.76E-08 & 19,537 & 26.8 \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
+\subsubsection{Griewank Benchmark Function Experiment}
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig_fun_griewank.pdf}
+    \caption{Box and whisker chart for the Griewank Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_griewank}
+    \end{figure}
+
+\begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Griewank Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_griewank5}
+    \begin{tabular}{@{}lllll@{}}
+    \toprule
+    \multicolumn{5}{l}{\textbf{Function Griewank - 5 Dimensions}} \\ \midrule
+     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
+    \textbf{Xover Mutation} & 6.92E-08 & 2.40E-08 & 44,566 & 48.3 \\
+    \textbf{Elite Projection} & 3.77E-08 & 2.74E-08 & 16,412 & 20.1 \\
+    \textbf{All Random} & 5.63E-08 & 2.99E-08 & 35,761 & 38.5 \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
+\begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Griewank Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_griewank10}
+    \begin{tabular}{@{}lllll@{}}
+    \toprule
+    \multicolumn{5}{l}{\textbf{Function Griewank - 10 Dimensions}} \\ \midrule
+     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
+    \textbf{Xover Mutation} & 8.07E-08 & 1.39E-08 & 92,885 & 100.0 \\
+    \textbf{Elite Projection} & 4.21E-08 & 3.40E-08 & 13,534 & 17.3 \\
+    \textbf{All Random} & 5.08E-08 & 3.54E-08 & 40,544 & 52.5 \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
+\subsubsection{Rastrigin Benchmark Function Experiment}
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig_fun_rastrigin.pdf}
+    \caption{Box and whisker chart for the Rastrigin Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_rastrigin}
+    \end{figure}
+
+\begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Rastrigin Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_rastrigin5}
+    \begin{tabular}{@{}lllll@{}}
+    \toprule
+    \multicolumn{5}{l}{\textbf{Function Rastrigin - 5 Dimensions}} \\ \midrule
+     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
+    \textbf{Xover Mutation} & 7.85E-08 & 1.59E-08 & 22,322 & 34.1 \\
+    \textbf{Elite Projection} & 4.42E-08 & 3.26E-08 & 10,860 & 14.8 \\
+    \textbf{All Random} & 5.66E-08 & 2.81E-08 & 21,122 & 35.0 \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
+\begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Rastrigin Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_rastrigin10}
+    \begin{tabular}{@{}lllll@{}}
+    \toprule
+    \multicolumn{5}{l}{\textbf{Function Rastrigin - 10   Dimensions}} \\ \midrule
+     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
+    \textbf{Xover Mutation} & 8.56E-08 & 1.23E-08 & 53,579 & 58.7 \\
+    \textbf{Elite Projection} & 3.17E-08 & 2.57E-08 & 8,704 & 13.0 \\
+    \textbf{All Random} & 5.00E-08 & 3.16E-08 & 24,376 & 27.4 \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
+\subsubsection{Sphere Benchmark Function Experiment}
+
+\begin{figure}
+    \includegraphics[width=\textwidth]{img/fig_fun_sphere.pdf}
+    \caption{Box and whisker chart for the Sphere Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_sphere}
+    \end{figure}
+
+\begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Sphere Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_sphere5}
+    \begin{tabular}{@{}lllll@{}}
+    \toprule
+    \multicolumn{5}{l}{\textbf{Function Sphere - 5 Dimensions}} \\ \midrule
+     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
+    \textbf{Xover Mutation} & 7.82E-08 & 1.65E-08 & 11,312 & 14.5 \\
+    \textbf{Elite Projection} & 3.60E-08 & 3.27E-08 & 7,056 & 10.9 \\
+    \textbf{All Random} & 6.14E-08 & 2.79E-08 & 9,158 & 12.2 \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
+\begin{table}[]
+    \scriptsize
+    \centering
+    \caption{Sphere Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_sphere10}
+    \begin{tabular}{@{}lllll@{}}
+    \toprule
+    \multicolumn{5}{l}{\textbf{Function Sphere - 10 Dimensions}} \\ \midrule
+     & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
+    \textbf{Xover Mutation} & 8.39E-08 & 1.45E-08 & 30,769 & 34.4 \\
+    \textbf{Elite Projection} & 4.28E-08 & 3.06E-08 & 9,236 & 13.3 \\
+    \textbf{All Random} & 5.32E-08 & 3.38E-08 & 21,465 & 26.3 \\ \bottomrule
+    \end{tabular}
+    \end{table}
+
 \subsection{ALTO / HASTA AQUI VAMOS}
+
+\section{Discussion}
+\label{section.discussion}
+
+At some crucial moments during our research, we got the feeling we were doing
+nature reverse engineering. One strategy was to let our imagination run wild
+and go for the simple solution. One of our earlier experiment's findings was to
+find balance, like the yin and yang, between death and reproduction.
+
+In our experiments, we found that when solving simple problems, the cost of
+communication between containers can become a factor to increase the total
+performance time, even though, we believe that the opposite must also be true.
+When solving complex problems, distributing the work on multiple resources
+should reduce throughput time, making the communication cost negligible.
+
+We must acknowledge the performance time of the DEAP library
+\cite{fortin2012deap} is highly efficient and short, due in part because the
+processing work execution is on a single processor with multiple cores, where
+the communication time is nearly non-existent. In contrast, our algorithm
+implementation requires a minimum of five containers and a message queue
+server. Even though the container work has proven to be very effective and
+efficient \cite{merelo2016performance,valdez2021container}, we must consider
+some time was added to our experiments by the minimal delays (in the thousands
+of a second magnitude) we used to keep the process execution relatively random,
+to mimic how the life-cycle stages work in nature \cite{read1968system}. As
+future work, we could test the Life-Cycle algorithm behavior by eliminating all
+remaining delays.
+
+This scheme allows for multiple parameter's fine tuning, granting us the
+freedom to experiment with different selection and reproduction strategies
+simultaneously, which will impact how fast it finds the solution and the
+obtained quality.
+
+\section{Conclusions}
+\label{section.conclusions}
+
+We implemented the algorithm with Docker containers by solving the OneMax
+problem comparing it with a traditional (sequential) GA algorithm, where it
+showed favorable and promising results. To further validate this work, we could
+use control or some more complex and demanding problem that requires computing
+real numbers \cite{stanley2002evolving,miikkulainen2019evolving}.
+
+As the complexity of problems increases, it is essential to have a scalable,
+replicable, and fault-tolerant model that uses collaborative techniques to work
+in the cloud, where multiple resources will be communicating asynchronously.
+This research has shown that it is possible to evolve a population of
+individuals, similar to a Genetic Algorithm (GA), using a distributed,
+parallel, and asynchronous methodology.
 
@@
 
-\subsection{Experiment Configuration}
-
-\subsection{Experiment Results}
-
-For each experiment, we ran 60 independent executions per algorithm and
-recorded the following results: Last Generation, Total Evaluations, Time
-(seconds), Evaluations/second. The labels used on the results of our summarized
-experiments tables are the following:
-
-\begin{itemize}
-    \item   Last Gen.   is the generation that found the solution.
-    \item   Eval.       is the total number of evaluations the algorithm executed. 
-    \item   Time (sec)  is the total elapsed or wall clock time, in seconds. 
-    \item   Eval/sec    is the calculated rate of evaluations per second.
-\end{itemize}
+\subsection{Experiment Example}
 
@@
 
-\section{Discussion}
-\label{section.discussion}
-
-At some crucial moments during our research, we got the feeling we were doing
-nature reverse engineering. One strategy was to let our imagination run wild
-and go for the simple solution. One of our earlier experiment's findings was to
-find balance, like the yin and yang, between death and reproduction.
-
-In our experiments, we found that when solving simple problems, the cost of
-communication between containers can become a factor to increase the total
-performance time, even though, we believe that the opposite must also be true.
-When solving complex problems, distributing the work on multiple resources
-should reduce throughput time, making the communication cost negligible.
-
-We must acknowledge the performance time of the DEAP library
-\cite{fortin2012deap} is highly efficient and short, due in part because the
-processing work execution is on a single processor with multiple cores, where
-the communication time is nearly non-existent. In contrast, our algorithm
-implementation requires a minimum of five containers and a message queue
-server. Even though the container work has proven to be very effective and
-efficient \cite{merelo2016performance,valdez2021container}, we must consider
-some time was added to our experiments by the minimal delays (in the thousands
-of a second magnitude) we used to keep the process execution relatively random,
-to mimic how the life-cycle stages work in nature \cite{read1968system}. As
-future work, we could test the Life-Cycle algorithm behavior by eliminating all
-remaining delays.
-
-This scheme allows for multiple parameter's fine tuning, granting us the
-freedom to experiment with different selection and reproduction strategies
-simultaneously, which will impact how fast it finds the solution and the
-obtained quality.
-
-\section{Conclusions}
-\label{section.conclusions}
-
-We implemented the algorithm with Docker containers by solving the OneMax
-problem comparing it with a traditional (sequential) GA algorithm, where it
-showed favorable and promising results. To further validate this work, we could
-use control or some more complex and demanding problem that requires computing
-real numbers \cite{stanley2002evolving,miikkulainen2019evolving}.
-
-As the complexity of problems increases, it is essential to have a scalable,
-replicable, and fault-tolerant model that uses collaborative techniques to work
-in the cloud, where multiple resources will be communicating asynchronously.
-This research has shown that it is possible to evolve a population of
-individuals, similar to a Genetic Algorithm (GA), using a distributed,
-parallel, and asynchronous methodology.
-
 \begin{acknowledgement}

### 2022-09-23 paper.tex
Updated Experiments
Work in progress

@@
     \toprule
-    \multicolumn{5}{l}{\textbf{Function Bohachevsky - 5 Dimensions}} \\ \midrule
+    \multicolumn{5}{l}{\textbf{Bohachevsky Function - 5 Dimensions}} \\ \midrule
      & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
@@
     \toprule
-    \multicolumn{5}{l}{\textbf{Function Bohachevsky - 10   Dimensions}} \\ \midrule
+    \multicolumn{5}{l}{\textbf{Bohachevsky Function - 10 Dimensions}} \\ \midrule
      & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
@@
     \toprule
-    \multicolumn{5}{l}{\textbf{Function Griewank - 5 Dimensions}} \\ \midrule
+    \multicolumn{5}{l}{\textbf{Griewank Function - 5 Dimensions}} \\ \midrule
      & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
@@
     \toprule
-    \multicolumn{5}{l}{\textbf{Function Griewank - 10 Dimensions}} \\ \midrule
+    \multicolumn{5}{l}{\textbf{Griewank Function - 10 Dimensions}} \\ \midrule
      & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
@@
     \toprule
-    \multicolumn{5}{l}{\textbf{Function Rastrigin - 5 Dimensions}} \\ \midrule
+    \multicolumn{5}{l}{\textbf{Rastrigin Function - 5 Dimensions}} \\ \midrule
      & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
@@
     \toprule
-    \multicolumn{5}{l}{\textbf{Function Rastrigin - 10   Dimensions}} \\ \midrule
+    \multicolumn{5}{l}{\textbf{Rastrigin Function - 10   Dimensions}} \\ \midrule
      & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
@@
     \toprule
-    \multicolumn{5}{l}{\textbf{Function Sphere - 5 Dimensions}} \\ \midrule
+    \multicolumn{5}{l}{\textbf{Sphere Function - 5 Dimensions}} \\ \midrule
      & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
@@
     \toprule
-    \multicolumn{5}{l}{\textbf{Function Sphere - 10 Dimensions}} \\ \midrule
+    \multicolumn{5}{l}{\textbf{Sphere Function - 10 Dimensions}} \\ \midrule
      & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\

### 2022-09-23 paper.tex
Updated Experiments
Graphics improvement.

@@
 
-\usepackage{booktabs}       %Booktabs Table Style
+\usepackage{booktabs}       % Booktabs Table Style
+
+\usepackage{graphicx}       % To frame graphic images
+\usepackage[export]{adjustbox}
 
@@
 
+The goal of our fist experiment was to have fun, while improving the graphics with best images.
+
 \begin{figure}
-    \includegraphics[width=\textwidth]{img/fig_fun_ackley.pdf}
+    \includegraphics[width=\linewidth, frame]{img/fig_fun_ackley.pdf}
     \caption{Box and whisker chart for the Ackley Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_ackley}
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{img/fig_fun_bohachevsky.pdf}
+    \includegraphics[width=\linewidth, frame]{img/fig_fun_bohachevsky.pdf}
     \caption{Box and whisker chart for the Bohachevsky Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_bohachevsky}
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{img/fig_fun_griewank.pdf}
+    \includegraphics[width=\linewidth, frame]{img/fig_fun_griewank.pdf}
     \caption{Box and whisker chart for the Griewank Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_griewank}
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{img/fig_fun_rastrigin.pdf}
+    \includegraphics[width=\linewidth, frame]{img/fig_fun_rastrigin.pdf}
     \caption{Box and whisker chart for the Rastrigin Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_rastrigin}
@@
 \begin{figure}
-    \includegraphics[width=\textwidth]{img/fig_fun_sphere.pdf}
+    \includegraphics[width=\linewidth, frame]{img/fig_fun_sphere.pdf}
     \caption{Box and whisker chart for the Sphere Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_sphere}

### 2022-09-23 paper.tex
Updated Experiments
Rosenbrock Function now included.

@@
 
+\subsubsection{Rosenbrock Benchmark Function Experiment}
+
+    \begin{figure}
+        \includegraphics[width=\linewidth, frame]{img/fig_fun_rosenbrock_5d.pdf}
+        \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 5 Dimensions.} \label{fig.fun_rosenbrock_5d}
+        \end{figure}
+
+    \begin{figure}
+        \includegraphics[width=\linewidth, frame]{img/fig_fun_rosenbrock_10d.pdf}
+        \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 10 Dimensions.} \label{fig.fun_rosenbrock_10d}
+        \end{figure}
+
 \subsection{ALTO / HASTA AQUI VAMOS}

### 2022-09-23 paper.tex
Updated Experiments
Rosenbrock tables included.

@@
 
+    \begin{table}[]
+        \scriptsize
+        \centering
+        \caption{Rosenbrock Benchmark Function summarized experiments table for 5 Dimensions.}\label{tab.fun_rosenbrock5}
+        \begin{tabular}{@{}lllll@{}}
+        \toprule
+        \multicolumn{5}{l}{\textbf{Function Rosenbrock - 5 Dimensions}} \\ \midrule
+        & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
+        \textbf{Xover Mutation} & 4.65E-03 & 8.29E-03 & 500,000 & 646.4 \\
+        \textbf{Elite Projection} & 9.62E-07 & 1.86E-06 & 307,878 & 427.0 \\
+        \textbf{All Random} & 8.30E-06 & 1.58E-05 & 491,400 & 697.8 \\ \bottomrule
+        \end{tabular}
+        \end{table}
+
     \begin{figure}
@@
         \end{figure}
+
+    \begin{table}[]
+        \scriptsize
+        \centering
+        \caption{Rosenbrock Benchmark Function summarized experiments table for 10 Dimensions.}\label{tab.fun_rosenbrock10}        
+        \begin{tabular}{@{}lllll@{}}
+        \toprule
+        \multicolumn{5}{l}{\textbf{Function Rosenbrock - 10 Dimensions}} \\ \midrule
+        & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
+        \textbf{Xover Mutation} & 1.35E+00 & 9.83E-01 & 1,000,000 & 1,384.3 \\
+        \textbf{Elite Projection} & 4.26E-02 & 4.34E-02 & 1,000,000 & 1,146.0 \\
+        \textbf{All Random} & 4.27E-02 & 6.02E-02 & 952,038 & 1,147.8 \\ \bottomrule
+        \end{tabular}
+        \end{table}
 

### 2022-09-23 paper.tex
Updated Tabulation
Work in progress. Reading improvement.
Updated Experiments
Work in progress.

@@
                 \toprule
-        \multicolumn{5}{l}{\textbf{Function Rosenbrock - 5 Dimensions}} \\ \midrule
+                \multicolumn{5}{l}{\textbf{Rosenbrock Function - 5 Dimensions}} \\ \midrule
                 & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\
@@
                 \toprule
-        \multicolumn{5}{l}{\textbf{Function Rosenbrock - 10 Dimensions}} \\ \midrule
+                \multicolumn{5}{l}{\textbf{Rosenbrock Function - 10 Dimensions}} \\ \midrule
                 & \textbf{Error} & \textbf{St-Dev} & \textbf{Evals.} & \textbf{Time} \\

### 2022-09-23 paper.tex
Updated Experiments
Work in progress.

@@
 Life-Cycle using ten processes (on containers) where we show the summarized
-results in Table~\ref{tab.experiment1}, and Figure~\ref{fig.experiment1} shows
+results in Table~\ref{tab.fun_ackley5}, and Figure~\ref{fig.fun_ackley} shows
 their Box and Whisker chart.
-
-\begin{table}[]
-    \centering        
-    \caption{Experiment 1 results: OneMax DEAP versus Life-Cycle (10 processes).}\label{tab.experiment1}
-    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
-    \hline
-    Run & \multicolumn{4}{l|}{OneMax DEAP} & \multicolumn{4}{l|}{Life-Cycle (10P)} \\ \hline
-    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
-    Avg. & 6.5 & 391 & 0.036 & 10,836 & 9.6 & 578 & 6.830 & 85 \\ \hline
-    \end{tabular}
-    \end{table}
-
-\begin{figure}
-    \fbox{\includegraphics[width=\textwidth]{img/fig6_experiment01_chart.pdf}}
-    \caption{Box and whisker chart for the Experiment 1: OneMax DEAP versus Life-Cycle.} \label{fig.experiment1}
-% You need to label axis y - JJ
-  \end{figure}
 
@@
 second configuration where we reduced the processes to the minimum basic 5. We
-show the summarized results in Table~\ref{tab.experiment2}, and
-Figure~\ref{fig.experiment2} shows their Box and Whisker chart.
-
-\begin{table}[]
-    \centering        
-    \caption{Experiment 2 results, Life-Cycle Tournament selection: 10 versus 5 processes.}\label{tab.experiment2}
-    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
-    \hline
-    Run & \multicolumn{4}{l|}{LifeCycle (Tourn. 10P)} & \multicolumn{4}{l|}{LifeCycle (Tourn. 5P)} \\ \hline
-    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
-    Avg. & 7.2 & 434 & 0.740 & 587 & 8.2 & 495 & 0.826 & 599 \\ \hline
-    \end{tabular}
-    \end{table}
-
-\begin{figure}
-    \fbox{\includegraphics[width=\textwidth]{img/fig7_experiment02_chart.pdf}}
-    \caption{Box and Whisker chart for the Experiment 2: Life-Cycle Tournament selection (10 versus 5 processes).} \label{fig.experiment2}
-    \end{figure}
+show the summarized results in Table~\ref{tab.fun_ackley5}, and
+Figure~\ref{fig.fun_ackley} shows their Box and Whisker chart.
 
@@
 goal approval range to 115. We show the summarized results in
-Table~\ref{tab.experiment3}, and Figure~\ref{fig.experiment3} shows their Box
+Table~\ref{tab.fun_ackley5}, and Figure~\ref{fig.fun_ackley} shows their Box
 and Whisker chart.
-
-\begin{table}[]
-    \centering        
-    \caption{Experiment 3 results, Life-Cycle Tournament: 6 processes (Death x2) versus 5 processes (80 to 115 goal).}\label{tab.experiment3}
-    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
-    \hline
-    Run & \multicolumn{4}{l|}{LifeCycle (Tourn. 6P, Death x2)} & \multicolumn{4}{l|}{LifeCycle (Tourn. 5P, 80-115g)} \\ \hline
-    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
-    Avg. & 8.0 & 483 & 0.846 & 571 & 6.4 & 384 & 0.695 & 553 \\ \hline
-    \end{tabular}
-    \end{table}
-
-\begin{figure}
-    \fbox{\includegraphics[width=\textwidth]{img/fig8_experiment03_chart.pdf}}
-    \caption{Box and Whisker chart for the Experiment 3: Life-Cycle Tournament (6 processes double Death, versus 5 processes with an 80 to 115 goal approval).} \label{fig.experiment3}
-    \end{figure}
 
@@
 approval range to 125. We show the summarized results in
-Table~\ref{tab.experiment4}, and Figure~\ref{fig.experiment4} shows their Box
+Table~\ref{tab.fun_ackley5}, and Figure~\ref{fig.fun_ackley} shows their Box
 and Whisker chart.
-
-\begin{table}[]
-    \centering        
-    \caption{Experiment 4 results, OneMax DEAP versus Life-Cycle Tournament: 5 processes (80 to 125 goal).}\label{tab.experiment4}
-    \begin{tabular}{|l|l|l|l|l|l|l|l|l|}
-    \hline
-    Run & \multicolumn{4}{l|}{OneMax DEAP} & \multicolumn{4}{l|}{Life-Cycle (Tourn. 5P, 80-125g)} \\ \hline
-    1-60 & Last Gen. & Eval. & Time (sec) & Eval/sec & Last Gen. & Eval. & Time (sec) & Eval/sec \\ \hline
-    Avg. & 6.5 & 391 & 0.036 & 10,836 & 6.3 & 377 & 0.678 & 556 \\ \hline
-    \end{tabular}
-    \end{table}
-
-\begin{figure}
-    \fbox{\includegraphics[width=\textwidth]{img/fig9_experiment4_chart.pdf}}
-    \caption{Box and Whisker chart for the Experiment 4: OneMax DEAP versus Life-Cycle Tournament (5 processes with an 80 to 125 goal approval).} \label{fig.experiment4}
-    \end{figure}
 

### 2022-09-23 paper.tex
Updated Paper
Work in progress.

@@
             \begin{figure}
-                \includegraphics[width=\linewidth, frame]{img/fig_fun_ackley.pdf}
+                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_ackley.pdf}
                 \caption{Box and whisker chart for the Ackley Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_ackley}
@@
             \begin{figure}
-                \includegraphics[width=\linewidth, frame]{img/fig_fun_bohachevsky.pdf}
+                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_bohachevsky.pdf}
                 \caption{Box and whisker chart for the Bohachevsky Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_bohachevsky}
@@
             \begin{figure}
-                \includegraphics[width=\linewidth, frame]{img/fig_fun_griewank.pdf}
+                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_griewank.pdf}
                 \caption{Box and whisker chart for the Griewank Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_griewank}
@@
             \begin{figure}
-                \includegraphics[width=\linewidth, frame]{img/fig_fun_rastrigin.pdf}
+                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rastrigin.pdf}
                 \caption{Box and whisker chart for the Rastrigin Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_rastrigin}
@@
             \begin{figure}
-                \includegraphics[width=\linewidth, frame]{img/fig_fun_sphere.pdf}
+                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_sphere.pdf}
                 \caption{Box and whisker chart for the Sphere Benchmark Function, 5 vs 10 Dimensions.} \label{fig.fun_sphere}
@@
             \begin{figure}
-                \includegraphics[width=\linewidth, frame]{img/fig_fun_rosenbrock_5d.pdf}
+                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rosenbrock_5d.pdf}
                 \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 5 Dimensions.} \label{fig.fun_rosenbrock_5d}
@@
             \begin{figure}
-                \includegraphics[width=\linewidth, frame]{img/fig_fun_rosenbrock_10d.pdf}
+                \includegraphics[width=0.99\linewidth, frame]{img/fig_fun_rosenbrock_10d.pdf}
                 \caption{Box and whisker chart for the Rosenbrock Benchmark Function, 10 Dimensions.} \label{fig.fun_rosenbrock_10d}

### 2022-09-23 paper.tex
Updated Visuals
Images and tables are now shown inside the corresponding section and subsection.

@@
 \usepackage[export]{adjustbox}
+
+\usepackage[section]{placeins} % Forces an image to be displayed in it's section
 
@@
 
-        \subsubsection{How does it work?} Based on the historically best candidate
+        \subsubsection{How does it work?}
+
+            Based on the historically best candidate
             solution and the elite set, we use the Golden Ratio (shown in
@@
                 \end{figure}
+
+            \FloatBarrier
 
@@
 
+            \FloatBarrier
+
         \subsubsection{Bohachevsky Benchmark Function Experiment}
@@
                 \end{table}
+
+            \FloatBarrier
 
@@
 
+            \FloatBarrier
+
         \subsubsection{Rastrigin Benchmark Function Experiment}
@@
 
+            \FloatBarrier
+
         \subsubsection{Sphere Benchmark Function Experiment}

### 2022-09-23 paper.tex
Updated Visuals
Work in progress.
Updated Box-Plot
Work in progress.
Updated Experiments
Improved experiment description.

@@
                 \includegraphics[width=0.65\textwidth]{img/fig_elite_projection.pdf}
-                \caption{Projection of the historically Elite solutions towards the Champion.} \label{fig.elite_projection}
+                \caption{Projection of an Elite solution (found on the right) towards the Champion (at the left).} \label{fig.elite_projection}
                 \end{figure}
@@
 
+        \FloatBarrier
+
     \subsection{Experiment Results}
@@
 
-            The goal of our fist experiment was to have fun, while improving the graphics with best images.
+            The goal of the first experiment was to confirm that this paper’s
+            proposed strategy obtained improved results over our basic
+            technique, which created a new population with a random generation
+            of a new set of candidate solutions. We chose Ackley as the first
+            Classic Benchmark Function for Optimization to test our algorithm
+            behavior, where Figure~\ref{fig.fun_ackley} shows its corresponding
+            Box and Whisker chart, and we summarized the results in
+            Table~\ref{tab.fun_ackley5} and Table~\ref{tab.fun_ackley10} (for
+            five and ten dimensions, respectively).
 

### 2022-09-24 paper.tex
Updated Experiments
Second experiment.

@@
 
+            As our second experiment to further validate and prove our
+            algorithm behavior, we chose Bohachevsky Classic Benchmark Function
+            for Optimization. Figure~\ref{fig.fun_bohachevsky} shows its
+            corresponding Box and Whisker chart, where we summarized the
+            results in Table~\ref{tab.fun_bohachevsky5} and
+            Table~\ref{tab.fun_bohachevsky10} (for five and ten dimensions,
+            respectively). Due to the observation and analysis of these
+            results, we identify our proposed strategy obtained solutions in
+            the same order as the traditional Xover Mutation, in a
+            significantly reduced number of evaluations.
+
             \begin{figure}

### 2022-09-24 paper.tex
Updated Experiment
Improved experiment description.

@@
 
+            The third experiment objective was to confirm Animal Life Cycle
+            Algorithm continued finding solutions in a reduced number of
+            evaluations. For this test, we selected the Griewank Benchmark
+            Function for Optimization. Figure~\ref{fig.fun_griewank} shows its
+            corresponding Box and Whisker chart, where we summarized the
+            results in Table~\ref{tab.fun_griewank5} and
+            Table~\ref{tab.fun_griewank10} (for five and ten dimensions,
+            respectively). With this analysis, we confirmed our strategy
+            continued to obtain solutions in the same order as expected, in a
+            reduced number of evaluations, in less time.
+
             \begin{figure}

### 2022-09-24 paper.tex
Updated Experiments
Improved experiment description.

@@
 
+            This experiment's goal was to follow and study the behavior of our
+            proposed strategy, to repeat the results in the same order as
+            expected, in a reduced number of both time and evaluations. We
+            selected Rastrigin Classic Benchmark Function for Optimization for
+            this experiment. Figure~\ref{fig.fun_rastrigin} shows its
+            corresponding Box and Whisker chart, where we summarized the
+            results in Table~\ref{tab.fun_rastrigin5} and
+            Table~\ref{tab.fun_rastrigin10} (for five and ten dimensions,
+            respectively).
+
             \begin{figure}
@@
 
-\subsubsection{Experiment 1} The goal of our first OneMax experiment was to
-make sure our Life-Cycle algorithm worked as expected, converging on the
-solution. For this experiment, we intentionally used delays (on the tenth of a
-second magnitude) to follow the Life-Cycle algorithm behavior on the console
-output. For this experiment, we compared the DEAP algorithm versus the
-Life-Cycle using ten processes (on containers) where we show the summarized
-results in Table~\ref{tab.fun_ackley5}, and Figure~\ref{fig.fun_ackley} shows
-their Box and Whisker chart.
-
-\subsubsection{Experiment 2} The goal of our second experiment was to confirm
-the Life-Cycle algorithm continued working as expected, converging on the
-solution. For this experiment, we reduced the time used on delays (now on the
-thousands of a second magnitude) to follow the Life-Cycle algorithm behavior.
-For this experiment, we only used tournament selection for the reproduction, on
-the first configuration running the Life-Cycle on ten processes, versus the
-second configuration where we reduced the processes to the minimum basic 5. We
-show the summarized results in Table~\ref{tab.fun_ackley5}, and
-Figure~\ref{fig.fun_ackley} shows their Box and Whisker chart.
-
-\subsubsection{Experiment 3} The goal of our third experiment was to follow and
-study the behavior of the Life-Cycle algorithm that continued converging on the
-solution. For this experiment, we remained using minimal delays (thousands of a
-second magnitude). For this experiment, we only used tournament selection for
-the reproduction, on the first configuration running the Life-Cycle on six
-processes, two of whom was the Death process, versus the second configuration
-where we reduced the processes to the minimum (five) but increasing the (Death)
-goal approval range to 115. We show the summarized results in
-Table~\ref{tab.fun_ackley5}, and Figure~\ref{fig.fun_ackley} shows their Box
-and Whisker chart.
-
 \subsubsection{Experiment 4} The goal of our fourth and last experiment was to

### 2022-09-24 paper.tex
Updated Experiment
Improved experiment description.

@@
 
+            For our fifth experiment we chose the Sphere Classic Benchmark
+            Function for Optimization. Even though the sphere function is
+            considered one of the simplest to solve, the same behavior was
+            consistent for the algorithm, where it showed a reduced number of
+            evaluations and execution time. We can confirm this affirmation
+            with the results shown in this experiment.
+            Figure~\ref{fig.fun_sphere} displays its corresponding Box and
+            Whisker chart, where we summarized the results in
+            Table~\ref{tab.fun_sphere5} and Table~\ref{tab.fun_sphere10} (for
+            five and ten dimensions, respectively).
+
             \begin{figure}
@@
         \subsubsection{Rosenbrock Benchmark Function Experiment}
+
+            AQUI.
 
@@
 
-%----------------------------------------------------
-%----------------------------------------------------
-%PREVIOUSLY / FROM THE FIRST CHAPTER
-%We designed our algorithm using observation, analysis, and abstraction in nature to identify what most species in the animal kingdom have in common, where individuals of a population that best adapt to the environment have greater chances of survival, reproduction, and improvement of the species.
-Imagining as if the task of writing these rules of evolution was in our hands, questioning how we could solve it?
-%Like nature, we identified what most species have in common in the life cycle.
-Our algorithm works on a constantly evolving population, experiencing the stages that all living beings undergo \cite{read1968system}: being born, growing up, reproducing, and dying, where each of these stages will be processes (of our algorithm) that randomly affect the population individuals, emulating the organic way.
-%Many of the publications with the most influence on our research ~\cite{valdez2021container,garcia2021event,merelo2016performance,merelo2016nodio} propose a cloud-native optimization architecture that features population-based algorithms.
-They present ideas such as those mentioned in Figure~\ref{fig.background}, which planted the seed of thought of our current paper.
-%Some questions in our train of thought were: How does nature work?
-Is evolution real?
-How do we enforce natural selection in evolution?
-What is the role of the attraction between couples on reproduction?
-How much of a factor is the attraction's role in the evolution of the species?
-What is the role of death in all of this?
-How much of an impact does death have on the evolution of a species?
-How do we include those ideas into our algorithm?
-%One of the main challenges when designing the algorithm was how to capture the essence of life by reflecting a population evolution?.
-In our minds, it was clear this task requires a combination of simultaneous working forces that influences the population improvement over time.
-Our strategy was simple: divide and conquer, looking into the clouds.
-Enter cloud-computing: previous cloud-computing algorithms have proven successful results working in optimization problems \cite{valdez2021container,garcia2021event}.
-%We turned back to our genetic algorithms knowledge, mixed with our inspiration and cloud computing, and designed the algorithm with the quest to divide the processing workload among multiple computers.
-This strategy would also make it possible to run our algorithm as a cloud service.
-Theoretically, one consequence of the workload distribution is to obtain lower execution times.
-%----------------------------------------------------
-%Birth: This algorithm starts with a randomly generated population, where the processes will interact with the population independently.
-This means that at any given time, any individual can experience any of these processes.
-Birth is the first process of our algorithm, and it is responsible for the initial generation of individuals.
-%Growth: As in nature, all individuals constantly grow, mature, or age.
-With increasing age, individuals may lose strength but also gain more knowledge to solve problems.
-We represent this with a possible mutation in each increment of age.
-The growth process will take an individual to assess whether it's ready to mature and undergo changes.
-%Reproduction: The attraction of a couple will depend on fitness: the better individual's fitness, the more attractive it will be, making it easier to find mating matches.
-This process will be taking random pairs of individuals to evaluate their attraction as a couple, to try to breed; when the gestation is successful, a new pair of individuals will be born (as the offspring).
-Not all couples will be compatible, so reproduction will not always be possible, but the problem arises: how to quantify the attraction between two individuals?
-%------------- We could have used several strategies to evaluate this attraction.
-Considering this algorithm takes a similar focus as the study of bacteria growth in microbiology, where we can observe and analyze the evolution of a population over time.
-As in nature' most species, the bigger a specimen is, the more attractive it is to its mating candidates.
-To be consistent with both ideas in our algorithm, we use the equation of Newton's Law of Universal Gravitation (1) to calculate the attraction between two individuals, where we visualize the individual fitness as its mass when using the equation.
-In previous work, Newton's Law of Universal Gravitation has shown success in helping to solve optimization problems \cite{sanchez2014fuzzy,rashedi2009gsa}.
-%Death: The death stage represents the challenges and adversities that life presents to overcome.
-This process evaluates the individual resistance to survive in the environment.
-The better fitness the individual has will increase its chances of survival.
-As time progresses, the demands of nature will also increase, pushing for only the best individuals to survive.
-%----------------------------------------------------
-%One strategic difference in our algorithm implementation is the reproduction process, which is flexible to work in parallel with multiple couple selection methods, for example, tournament selection, random selection (Closed Reproduction process), and couple match by creating a new mating individual (Open Reproduction process).
-We use many combinations of the containerized processes, up to the minimum number required to obtain good results.
-Figure~\ref{fig.processes_containers} shows a comparison of only two alternatives for the implementation of the algorithm.
-Our experimentation started with a configuration of ten processes and ended in five, shown on the left and right sides of Fig.~\ref{fig.processes_containers}, respectively.
-%In our four experiments, we needed to match or balance the experimentation parameters according to the specifications of the algorithm used by the DEAP library.
-This is to be able to verify if our algorithm would also converge on the solutions in a similar number of evaluations and execution time.
-Table~\ref{tab.configuration} shows the OneMax initial configuration for DEAP and Life-Cycle experiment.
-%----------------------------------------------------
-
-\section{Another Section}
-\label{section.another_section}
-
-\subsection{Experiment Example}
-
-\subsubsection{Experiment 4} The goal of our fourth and last experiment was to
-follow and study the behavior of the Life-Cycle algorithm that continued
-converging on the solution. For this experiment, we remained using minimal
-delays (thousands of a second magnitude). For this experiment, we compared the
-OneMax DEAP implementation versus the Life-Cycle algorithm, only using
-tournament selection for the reproduction, with the Life-Cycle configuration
-running on the minimum (five) processes but increasing the (Death) goal
-approval range to 125. We show the summarized results in
-Table~\ref{tab.fun_ackley5}, and Figure~\ref{fig.fun_ackley} shows their Box
-and Whisker chart.
-
 \begin{acknowledgement}
@@
 \end{document}
+
+%----------------------------------------------------
+%----------------------------------------------------
+% PREVIOUSLY / FROM THE FIRST CHAPTER
+% We designed our algorithm using observation, analysis, and abstraction in nature to identify what most species in the animal kingdom have in common, where individuals of a population that best adapt to the environment have greater chances of survival, reproduction, and improvement of the species.
+Imagining as if the task of writing these rules of evolution was in our hands, questioning how we could solve it?
+% Like nature, we identified what most species have in common in the life cycle.
+Our algorithm works on a constantly evolving population, experiencing the stages that all living beings undergo \cite{read1968system}: being born, growing up, reproducing, and dying, where each of these stages will be processes (of our algorithm) that randomly affect the population individuals, emulating the organic way.
+% Many of the publications with the most influence on our research ~\cite{valdez2021container,garcia2021event,merelo2016performance,merelo2016nodio} propose a cloud-native optimization architecture that features population-based algorithms.
+They present ideas such as those mentioned in Figure~\ref{fig.background}, which planted the seed of thought of our current paper.
+% Some questions in our train of thought were: How does nature work?
+Is evolution real?
+How do we enforce natural selection in evolution?
+What is the role of the attraction between couples on reproduction?
+How much of a factor is the attraction's role in the evolution of the species?
+What is the role of death in all of this?
+How much of an impact does death have on the evolution of a species?
+How do we include those ideas into our algorithm?
+% One of the main challenges when designing the algorithm was how to capture the essence of life by reflecting a population evolution?.
+In our minds, it was clear this task requires a combination of simultaneous working forces that influences the population improvement over time.
+Our strategy was simple: divide and conquer, looking into the clouds.
+Enter cloud-computing: previous cloud-computing algorithms have proven successful results working in optimization problems \cite{valdez2021container,garcia2021event}.
+% We turned back to our genetic algorithms knowledge, mixed with our inspiration and cloud computing, and designed the algorithm with the quest to divide the processing workload among multiple computers.
+This strategy would also make it possible to run our algorithm as a cloud service.
+Theoretically, one consequence of the workload distribution is to obtain lower execution times.
+%----------------------------------------------------
+% Birth: This algorithm starts with a randomly generated population, where the processes will interact with the population independently.
+This means that at any given time, any individual can experience any of these processes.
+Birth is the first process of our algorithm, and it is responsible for the initial generation of individuals.
+% Growth: As in nature, all individuals constantly grow, mature, or age.
+With increasing age, individuals may lose strength but also gain more knowledge to solve problems.
+We represent this with a possible mutation in each increment of age.
+The growth process will take an individual to assess whether it's ready to mature and undergo changes.
+% Reproduction: The attraction of a couple will depend on fitness: the better individual's fitness, the more attractive it will be, making it easier to find mating matches.
+This process will be taking random pairs of individuals to evaluate their attraction as a couple, to try to breed; when the gestation is successful, a new pair of individuals will be born (as the offspring).
+Not all couples will be compatible, so reproduction will not always be possible, but the problem arises: how to quantify the attraction between two individuals?
+% .............
+We could have used several strategies to evaluate this attraction.
+Considering this algorithm takes a similar focus as the study of bacteria growth in microbiology, where we can observe and analyze the evolution of a population over time.
+As in nature' most species, the bigger a specimen is, the more attractive it is to its mating candidates.
+To be consistent with both ideas in our algorithm, we use the equation of Newton's Law of Universal Gravitation (1) to calculate the attraction between two individuals, where we visualize the individual fitness as its mass when using the equation.
+In previous work, Newton's Law of Universal Gravitation has shown success in helping to solve optimization problems \cite{sanchez2014fuzzy,rashedi2009gsa}.
+% Death: The death stage represents the challenges and adversities that life presents to overcome.
+This process evaluates the individual resistance to survive in the environment.
+The better fitness the individual has will increase its chances of survival.
+As time progresses, the demands of nature will also increase, pushing for only the best individuals to survive.
+% ----------------------------------------------------
+% One strategic difference in our algorithm implementation is the reproduction process, which is flexible to work in parallel with multiple couple selection methods, for example, tournament selection, random selection (Closed Reproduction process), and couple match by creating a new mating individual (Open Reproduction process).
+We use many combinations of the containerized processes, up to the minimum number required to obtain good results.
+Figure~\ref{fig.processes_containers} shows a comparison of only two alternatives for the implementation of the algorithm.
+Our experimentation started with a configuration of ten processes and ended in five, shown on the left and right sides of Fig.~\ref{fig.processes_containers}, respectively.
+% In our four experiments, we needed to match or balance the experimentation parameters according to the specifications of the algorithm used by the DEAP library.
+This is to be able to verify if our algorithm would also converge on the solutions in a similar number of evaluations and execution time.
+Table~\ref{tab.configuration} shows the OneMax initial configuration for DEAP and Life-Cycle experiment.
+%----------------------------------------------------
+%----------------------------------------------------

### 2022-09-24 paper.tex
Updated Experiments
Improved experiment description.

@@
             Box and Whisker chart, and we summarized the results in
-            Table~\ref{tab.fun_ackley5} and Table~\ref{tab.fun_ackley10} (for
-            five and ten dimensions, respectively).
+            Tables~\ref{tab.fun_ackley5} and~\ref{tab.fun_ackley10} (for five 
+            and ten dimensions, respectively).
 
@@
             corresponding Box and Whisker chart, where we summarized the
-            results in Table~\ref{tab.fun_bohachevsky5} and
-            Table~\ref{tab.fun_bohachevsky10} (for five and ten dimensions,
-            respectively). Due to the observation and analysis of these
-            results, we identify our proposed strategy obtained solutions in
-            the same order as the traditional Xover Mutation, in a
-            significantly reduced number of evaluations.
+            results in Tables~\ref{tab.fun_bohachevsky5} and~\ref{tab.fun_bohachevsky10} 
+            (for five and ten dimensions, respectively). Due to the observation 
+            and analysis of these results, we identify our proposed strategy 
+            obtained solutions in the same order as the traditional Xover Mutation, 
+            in a significantly reduced number of evaluations.
 
@@
             corresponding Box and Whisker chart, where we summarized the
-            results in Table~\ref{tab.fun_griewank5} and
-            Table~\ref{tab.fun_griewank10} (for five and ten dimensions,
-            respectively). With this analysis, we confirmed our strategy
-            continued to obtain solutions in the same order as expected, in a
-            reduced number of evaluations, in less time.
+            results in Tables~\ref{tab.fun_griewank5} and~\ref{tab.fun_griewank10} 
+            (for five and ten dimensions, respectively). With this analysis, 
+            we confirmed our strategy continued to obtain solutions in the same 
+            order as expected, in a reduced number of evaluations, in less time.
 
@@
             corresponding Box and Whisker chart, where we summarized the
-            results in Table~\ref{tab.fun_rastrigin5} and
-            Table~\ref{tab.fun_rastrigin10} (for five and ten dimensions,
-            respectively).
+            results in Tables~\ref{tab.fun_rastrigin5} and~\ref{tab.fun_rastrigin10} 
+            (for five and ten dimensions, respectively).
 
@@
             Whisker chart, where we summarized the results in
-            Table~\ref{tab.fun_sphere5} and Table~\ref{tab.fun_sphere10} (for
+            Tables~\ref{tab.fun_sphere5} and~\ref{tab.fun_sphere10} (for
             five and ten dimensions, respectively).
@@
 
-            AQUI.
+            The goal of our sixth and last experiment was to study the behavior
+            of the Animal Life-Cycle Algorithm when tested with the Rosenbrock
+            Benchmark Function for Optimization. From all of our previous
+            evaluation functions, Rosenbrock presented the most difficult
+            challenge for our algorithm. This test facilitated the
+            differentiation between the three compared strategies because the
+            solutions found were in different numeric order. After all tests,
+            the Elite Projection proved to be the best alternative. We can
+            corroborate this by analyzing Figures~\ref{fig.fun_rosenbrock_5d}
+            and~\ref{fig.fun_rosenbrock_10d}, which shows its corresponding Box
+            and Whisker chart. We present the summarized results in
+            Tables~\ref{tab.fun_rosenbrock5} and~\ref{tab.fun_rosenbrock10}
+            (for five and ten dimensions, respectively).
 

### 2022-09-24 paper.tex
Update Paper
Experiment section completed. Beginning with the Discussion.
Updated Paper
Work in progress.

@@
             we confirmed our strategy continued to obtain solutions in the same 
-            order as expected, in a reduced number of evaluations, in less time.
+            order as expected, in a reduced number of evaluations and less time.
 
@@
 
-    \subsection{ALTO / HASTA AQUI VAMOS}
-
 \section{Discussion}
 \label{section.discussion}
+
+***********************
+ALTO / HASTA AQUI VAMOS
+***********************
 

### 2022-09-25 paper.tex
Updated Discussion
Work in progress.

@@
 
+    Imagine being an astronaut on a mission repairing a space station in the
+    middle of space. Suddenly, a block of asteroids hits the craft, and you
+    lose your oxygen tank while the explosion pushes you away. From afar, you
+    see the area where your tank might be, covered with something similar to a
+    gas leaked from the station that blocks all visibility. Finding the tank is
+    the only hope to return to your main ship some miles away. The oxygen
+    reserve from your suit is running out, and there are only a couple of
+    minutes left. Now hold your breath in real life and think, what strategy
+    will you choose to search for your tank? We repeated this mental exercise
+    several times until we found the best solution (or blacked out).
+
+    If your life depended on it, would you choose a Genetic Algorithm, a
+    variant of a Particle Swarm Optimization Algorithm, or another? We searched
+    for a way to mix both, at least in some way, take the main idea or concepts
+    from them and make them work together. We strongly believe it is possible
+    to combine the features, as previous work has proven to obtain outstanding
+    results \cite{garcia2015evospace,garcia2021event,valdez2021container,valdez2021swarm}.
+    Our goal was to create a swarm out of the best individuals found in
+    evolution. We probably have a long way to go, but at least we are getting
+    promising results. From our experiments, all six Classic Benchmark
+    Functions for Optimization (Ackley, Bohachevsky, Griewank, Rastrigin,
+    Sphere, and Rosenbrock) proved the same behavior for the Animal Life Cycle
+    Algorithm: finding the expected solution in a reduced number of evaluations
+    and less execution time.
+
+\section{Conclusions}
+\label{section.conclusions}
+
 ***********************
@@
 ***********************
-
-At some crucial moments during our research, we got the feeling we were doing
-nature reverse engineering. One strategy was to let our imagination run wild
-and go for the simple solution. One of our earlier experiment's findings was to
-find balance, like the yin and yang, between death and reproduction.
-
-In our experiments, we found that when solving simple problems, the cost of
-communication between containers can become a factor to increase the total
-performance time, even though, we believe that the opposite must also be true.
-When solving complex problems, distributing the work on multiple resources
-should reduce throughput time, making the communication cost negligible.
-
-We must acknowledge the performance time of the DEAP library
-\cite{fortin2012deap} is highly efficient and short, due in part because the
-processing work execution is on a single processor with multiple cores, where
-the communication time is nearly non-existent. In contrast, our algorithm
-implementation requires a minimum of five containers and a message queue
-server. Even though the container work has proven to be very effective and
-efficient \cite{merelo2016performance,valdez2021container}, we must consider
-some time was added to our experiments by the minimal delays (in the thousands
-of a second magnitude) we used to keep the process execution relatively random,
-to mimic how the life-cycle stages work in nature \cite{read1968system}. As
-future work, we could test the Life-Cycle algorithm behavior by eliminating all
-remaining delays.
-
-This scheme allows for multiple parameter's fine tuning, granting us the
-freedom to experiment with different selection and reproduction strategies
-simultaneously, which will impact how fast it finds the solution and the
-obtained quality.
-
-\section{Conclusions}
-\label{section.conclusions}
 
@@
 %----------------------------------------------------
+%At some crucial moments during our research, we got the feeling we were doing nature reverse engineering.
+One strategy was to let our imagination run wild and go for the simple solution.
+One of our earlier experiment's findings was to find balance, like the yin and yang, between death and reproduction.
+%In our experiments, we found that when solving simple problems, the cost of communication between containers can become a factor to increase the total performance time, even though, we believe that the opposite must also be true.
+When solving complex problems, distributing the work on multiple resources should reduce throughput time, making the communication cost negligible.
+%We must acknowledge the performance time of the DEAP library \cite{fortin2012deap} is highly efficient and short, due in part because the processing work execution is on a single processor with multiple cores, where the communication time is nearly non-existent.
+In contrast, our algorithm implementation requires a minimum of five containers and a message queue server.
+Even though the container work has proven to be very effective and efficient \cite{merelo2016performance,valdez2021container}, we must consider some time was added to our experiments by the minimal delays (in the thousands of a second magnitude) we used to keep the process execution relatively random, to mimic how the life-cycle stages work in nature \cite{read1968system}.
+%This scheme allows for multiple parameter's fine tuning, granting us the freedom to experiment with different selection and reproduction strategies simultaneously, which will impact how fast it finds the solution and the obtained quality.
+%As future work, we could test the Life-Cycle algorithm behavior by eliminating all remaining delays.
 %----------------------------------------------------
+%---------------------------------------------------- garcia2015evospace  garcia2021event  valdez2021container  valdez2021swarm

### 2022-09-25 paper.tex
First Draft Completed.
First draft submission.

@@
 
-***********************
-ALTO / HASTA AQUI VAMOS
-***********************
+    The Animal Life Cycle Algorithm allows for multiple parameters'
+    fine-tuning, facilitating the freedom to experiment with different
+    alternatives to restart the population and solve extinction caused by
+    nature's pressure, which will impact how quickly, and the quality of its
+    solution found. We compared the results obtained with the use of historical
+    elite projection versus other alternatives, using classic benchmark
+    functions for optimization for comparison, where it showed favorable and
+    promising results.
 
-We implemented the algorithm with Docker containers by solving the OneMax
-problem comparing it with a traditional (sequential) GA algorithm, where it
-showed favorable and promising results. To further validate this work, we could
-use control or some more complex and demanding problem that requires computing
-real numbers \cite{stanley2002evolving,miikkulainen2019evolving}.
-
-As the complexity of problems increases, it is essential to have a scalable,
-replicable, and fault-tolerant model that uses collaborative techniques to work
-in the cloud, where multiple resources will be communicating asynchronously.
-This research has shown that it is possible to evolve a population of
-individuals, similar to a Genetic Algorithm (GA), using a distributed,
-parallel, and asynchronous methodology.
+    As the complexity of problems increases, it is essential to have a
+    scalable, replicable, and fault-tolerant model that uses collaborative
+    techniques to work in the cloud, where multiple resources will be
+    communicating asynchronously. This research has shown that it is possible
+    to evolve a population of individuals, similar to a Genetic Algorithm (GA),
+    using a distributed, parallel, and asynchronous methodology. To further
+    validate this work, we could use control or some more complex and demanding
+    problem that requires calculating real numbers
+    \cite{stanley2002evolving,miikkulainen2019evolving}. We implemented the
+    algorithm using Docker containers.
 
@@
 
-%----------------------------------------------------
-%----------------------------------------------------
-% PREVIOUSLY / FROM THE FIRST CHAPTER
-% We designed our algorithm using observation, analysis, and abstraction in nature to identify what most species in the animal kingdom have in common, where individuals of a population that best adapt to the environment have greater chances of survival, reproduction, and improvement of the species.
-Imagining as if the task of writing these rules of evolution was in our hands, questioning how we could solve it?
-% Like nature, we identified what most species have in common in the life cycle.
-Our algorithm works on a constantly evolving population, experiencing the stages that all living beings undergo \cite{read1968system}: being born, growing up, reproducing, and dying, where each of these stages will be processes (of our algorithm) that randomly affect the population individuals, emulating the organic way.
-% Many of the publications with the most influence on our research ~\cite{valdez2021container,garcia2021event,merelo2016performance,merelo2016nodio} propose a cloud-native optimization architecture that features population-based algorithms.
-They present ideas such as those mentioned in Figure~\ref{fig.background}, which planted the seed of thought of our current paper.
-% Some questions in our train of thought were: How does nature work?
-Is evolution real?
-How do we enforce natural selection in evolution?
-What is the role of the attraction between couples on reproduction?
-How much of a factor is the attraction's role in the evolution of the species?
-What is the role of death in all of this?
-How much of an impact does death have on the evolution of a species?
-How do we include those ideas into our algorithm?
-% One of the main challenges when designing the algorithm was how to capture the essence of life by reflecting a population evolution?.
-In our minds, it was clear this task requires a combination of simultaneous working forces that influences the population improvement over time.
-Our strategy was simple: divide and conquer, looking into the clouds.
-Enter cloud-computing: previous cloud-computing algorithms have proven successful results working in optimization problems \cite{valdez2021container,garcia2021event}.
-% We turned back to our genetic algorithms knowledge, mixed with our inspiration and cloud computing, and designed the algorithm with the quest to divide the processing workload among multiple computers.
-This strategy would also make it possible to run our algorithm as a cloud service.
-Theoretically, one consequence of the workload distribution is to obtain lower execution times.
-%----------------------------------------------------
-% Birth: This algorithm starts with a randomly generated population, where the processes will interact with the population independently.
-This means that at any given time, any individual can experience any of these processes.
-Birth is the first process of our algorithm, and it is responsible for the initial generation of individuals.
-% Growth: As in nature, all individuals constantly grow, mature, or age.
-With increasing age, individuals may lose strength but also gain more knowledge to solve problems.
-We represent this with a possible mutation in each increment of age.
-The growth process will take an individual to assess whether it's ready to mature and undergo changes.
-% Reproduction: The attraction of a couple will depend on fitness: the better individual's fitness, the more attractive it will be, making it easier to find mating matches.
-This process will be taking random pairs of individuals to evaluate their attraction as a couple, to try to breed; when the gestation is successful, a new pair of individuals will be born (as the offspring).
-Not all couples will be compatible, so reproduction will not always be possible, but the problem arises: how to quantify the attraction between two individuals?
-% .............
-We could have used several strategies to evaluate this attraction.
-Considering this algorithm takes a similar focus as the study of bacteria growth in microbiology, where we can observe and analyze the evolution of a population over time.
-As in nature' most species, the bigger a specimen is, the more attractive it is to its mating candidates.
-To be consistent with both ideas in our algorithm, we use the equation of Newton's Law of Universal Gravitation (1) to calculate the attraction between two individuals, where we visualize the individual fitness as its mass when using the equation.
-In previous work, Newton's Law of Universal Gravitation has shown success in helping to solve optimization problems \cite{sanchez2014fuzzy,rashedi2009gsa}.
-% Death: The death stage represents the challenges and adversities that life presents to overcome.
-This process evaluates the individual resistance to survive in the environment.
-The better fitness the individual has will increase its chances of survival.
-As time progresses, the demands of nature will also increase, pushing for only the best individuals to survive.
-% ----------------------------------------------------
-% One strategic difference in our algorithm implementation is the reproduction process, which is flexible to work in parallel with multiple couple selection methods, for example, tournament selection, random selection (Closed Reproduction process), and couple match by creating a new mating individual (Open Reproduction process).
-We use many combinations of the containerized processes, up to the minimum number required to obtain good results.
-Figure~\ref{fig.processes_containers} shows a comparison of only two alternatives for the implementation of the algorithm.
-Our experimentation started with a configuration of ten processes and ended in five, shown on the left and right sides of Fig.~\ref{fig.processes_containers}, respectively.
-% In our four experiments, we needed to match or balance the experimentation parameters according to the specifications of the algorithm used by the DEAP library.
-This is to be able to verify if our algorithm would also converge on the solutions in a similar number of evaluations and execution time.
-Table~\ref{tab.configuration} shows the OneMax initial configuration for DEAP and Life-Cycle experiment.
-%----------------------------------------------------
-%At some crucial moments during our research, we got the feeling we were doing nature reverse engineering.
-One strategy was to let our imagination run wild and go for the simple solution.
-One of our earlier experiment's findings was to find balance, like the yin and yang, between death and reproduction.
-%In our experiments, we found that when solving simple problems, the cost of communication between containers can become a factor to increase the total performance time, even though, we believe that the opposite must also be true.
-When solving complex problems, distributing the work on multiple resources should reduce throughput time, making the communication cost negligible.
-%We must acknowledge the performance time of the DEAP library \cite{fortin2012deap} is highly efficient and short, due in part because the processing work execution is on a single processor with multiple cores, where the communication time is nearly non-existent.
-In contrast, our algorithm implementation requires a minimum of five containers and a message queue server.
-Even though the container work has proven to be very effective and efficient \cite{merelo2016performance,valdez2021container}, we must consider some time was added to our experiments by the minimal delays (in the thousands of a second magnitude) we used to keep the process execution relatively random, to mimic how the life-cycle stages work in nature \cite{read1968system}.
-%This scheme allows for multiple parameter's fine tuning, granting us the freedom to experiment with different selection and reproduction strategies simultaneously, which will impact how fast it finds the solution and the obtained quality.
-%As future work, we could test the Life-Cycle algorithm behavior by eliminating all remaining delays.
-%----------------------------------------------------
-%---------------------------------------------------- garcia2015evospace  garcia2021event  valdez2021container  valdez2021swarm
+% TO-DO: Turniting.

### 2022-09-26 paper.tex
Updated Paper
Reduced similarity on Introduction and Conclusions.

@@
 
-    Bio-inspired algorithms have been very successful when used to solve complex
-    optimization problems
-    \cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but as
-    their complexity increases so does the computing power required to execute them
-    \cite{ontiveros2018high}. One strategy to address this processing need is to
-    use distributed computing \cite{thain2005distributed}, or the resources
-    available in the cloud to help find the solution
-    \cite{garcia2013there,eshratifar2019bottlenet}. This strategy gives us
-    elasticity to increase (or reduce) the computing power to achieve a balance
-    according to the nature of the problem.
+    Biologically inspired algorithms have proven to be very effective when
+    solving complex optimization problems
+    \cite{castillo2019comparative,valdez2021swarm,acherjee2020ultrasonic}, but
+    the more challenging the problem, the more computing power it will require
+    to solve them \cite{ontiveros2018high}. One technique to manage this
+    processing power is to use distributed computing
+    \cite{thain2005distributed} or the cloud available resources to help solve
+    the problem \cite{garcia2013there,eshratifar2019bottlenet}. This strategy
+    allows adaptation of the computing power according to the problem's
+    complexity.
 
-    Most bio-inspired algorithms are traditionally designed with a sequential
-    (synchronous) perspective \cite{porto2018evolutionary,back1996evolutionary},
-    where each process must wait for the previous task to finish before continuing.
-    Our proposal presents an algorithm in its entirety as a native solution in the
-    cloud, fully distributed, where its processes are executed in parallel and
-    asynchronously. We designed the algorithm as a cloud-native solution using the
-    cloud available resources to divide the processing workload, among several
-    computers or running the algorithm as a cloud service. This technique makes it
-    easy to scale the computing power according to the complexity required by the
-    problem \cite{armbrust2010view}.
+    Most frequently, bio-inspired algorithms are developed with a sequential
+    (synchronous) perspective
+    \cite{porto2018evolutionary,back1996evolutionary}, where a process must
+    pause for the previous job to finish before continuing. In this research,
+    we present an algorithm built as a native cloud solution, totally
+    distributed, where its processes are executed asynchronously and in
+    parallel. We designed the algorithm using the cloud available resources to
+    distribute the processing workload among several computers or as a service
+    in the cloud. This strategy allows to elastically increase (or reduce) the
+    computing power according to the nature of the challenge
+    \cite{armbrust2010view}.
 
@@
     nature's pressure, which will impact how quickly, and the quality of its
-    solution found. We compared the results obtained with the use of historical
+    found solution. We compared the results obtained with the use of historical
     elite projection versus other alternatives, using classic benchmark
@@
 
-    As the complexity of problems increases, it is essential to have a
-    scalable, replicable, and fault-tolerant model that uses collaborative
-    techniques to work in the cloud, where multiple resources will be
-    communicating asynchronously. This research has shown that it is possible
-    to evolve a population of individuals, similar to a Genetic Algorithm (GA),
-    using a distributed, parallel, and asynchronous methodology. To further
-    validate this work, we could use control or some more complex and demanding
+    As the nature of the challenge increases, it is indispensable to have an
+    elastic, scalable, and fault-tolerant model designed with cloud
+    collaboration processes, and asynchronous communication. We have proven
+    that it is possible to evolve a population, using a distributed, parallel,
+    and asynchronous strategy, inspired by the Genetic Algorithm (GA). To
+    further validate this work, we could use some more demanding (or control)
     problem that requires calculating real numbers

### 2022-09-30 paper.tex
Updated Paper
Similarity reduced on introduction and conclusion.
Updated similarity
Work in progress.
Updated Proposal
Work in progress.

@@
     the problem \cite{garcia2013there,eshratifar2019bottlenet}. This strategy
-    allows adaptation of the computing power according to the problem's
+    allows adaptating the required computing power according to the problem's
     complexity.
@@
 
-    Our inspiration for this algorithm was found in the study and observation of
-    nature, using general abstraction to identify what most animal species have in
-    common: the life cycle. We present an algorithm inspired by the biological
-    life-cycle of animal species, which consists of several stages
-    \cite{read1968system}: birth, growth, reproduction, and death. The combination
-    of those processes results in evolution. As in nature, we intend to execute all
-    these stages in parallel and asynchronously on a constantly evolving
+    In previous work, we presented an algorithm inspired by nature, where we
+    used observation, analysis, and abstraction to model our algorithm based on
+    the generalization of the life cycle of animal species. Our algorithm, as
+    in nature, consists of four stages \cite{read1968system}: birth, growth,
+    reproduction, and death. One key concept of our idea is that combining
+    those processes results in evolution. We propose to execute all these
+    stages in parallel and asynchronously on a continuously evolving
     population.
@@
 
-        This algorithm seeks to imitate the natural life cycle, where new individuals
-        are born at any moment and mature over time, where they age and then suffer
-        mutations throughout their lives. In reproduction, couples match by mutual
-        attraction. Death can happen to everyone: from a newborn to an aged adult,
-        where the individual's fitness will impact their longevity. We display the
-        general model concept in Figure~\ref{fig.algorithm_model}.
+        Our algorithm's goal is to mimic the animal life cycle, where at any
+        given moment, new individuals are born to be part of the population and
+        participate in the collective evolution. As time passes, they grow
+        older and mature, suffering changes throughout their lives that we
+        chose to represent as mutations. In our analysis, we considered a
+        couple's attraction a fundamental factor in reproduction. We thought of
+        death's work to maintain balance in the population by enforcing the
+        survival of the fittest. As in life, death can happen to everyone: from
+        a newborn to the elderly, where fitness will determine the individual's
+        longevity. We display the general model concept in
+        Figure~\ref{fig.algorithm_model}.
 

### 2022-09-30 paper.tex
Updated Proposal
Work in progress.

@@
 
-        \subsubsection{Birth} Birth is the first process of our algorithm, and it is
-        responsible for the initial generation of individuals. This algorithm starts
-        with a randomly generated population.
+        \subsubsection{Birth} Birth is the first step of the population's
+        evolution. For the algorithm representation, we begin with the
+        generation of a randomly set of individuals.
 

### 2022-09-30 paper.tex
Updated Proposal
Work in progress.

@@
 
-        \subsubsection{Growth} As in nature, all individuals constantly grow, mature,
-        or age. With increasing age, individuals may lose strength but may also gain
-        knowledge to solve problems. We represent this with a possible mutation in each
-        increment of age.
+        \subsubsection{Growth} In our algorithm representation, there is a
+        direct correlation between elapsed time and the population's evolution.
+        For this to be possible in our proposal, all individuals must grow
+        older and change as time progresses. With each increment of age, an
+        individual may improve or deteriorate. We chose to manifest this idea
+        by performing a small mutation in each change.
 

### 2022-09-30 paper.tex
Updated Proposal
Work in progress.

@@
 
-        \subsubsection{Reproduction} This process will select random pairs of
-        individuals to evaluate their attraction as a couple, where this attraction
-        will depend on fitness. The better individual's fitness, the more attractive it
-        will be. Not all couples will be compatible, so reproduction will not always be
-        possible. When the breeding is successful, a new pair of individuals will be
-        born (offspring).
+        \subsubsection{Reproduction} In this step, we select a random pair of
+        individuals and evaluate their couple's attraction, where fitness will
+        be the decisive factor that impacts its value. The higher the fitness
+        of the individual, the more attractive it will appear to fellow
+        individuals. As a consequence of the previous concept, we can
+        anticipate that not all couples will produce offspring, meaning
+        reproduction will not always be successful.
 

### 2022-09-30 paper.tex

@@
 
-        \subsubsection{Death} The death stage represents the challenges and adversities
-        that life presents. This process evaluates the individual resistance to survive
-        in the environment. The better fitness the individual has will increase its
-        chances of survival. As time progresses, the demands of nature will also
-        increase, pushing for only the best individuals to survive.
+        \subsubsection{Death} Death is the last step of the animal life cycle,
+        as in our algorithm. We chose death as a representation of all the
+        environmental challenges for survival, where its execution enforces the
+        survival of the fittest. As time progresses, so does increase nature's
+        level of danger. The better the individual fitness will increase its
+        chances of survival.
 

### 2022-09-30 paper.tex
Updated References
Also added contact email.

@@
 % your contribution title if the original one is too long
-\institute{J. C. Felix-Saul \at Tijuana Institute of Technology, Tijuana, Mexico, \email{name@email.address}
-\and Mario García Valdez \at Tijuana Institute of Technology, Tijuana, Mexico, \email{name@email.address}}
+\institute{J. C. Felix-Saul \at Tijuana Institute of Technology, Tijuana, Mexico, \email{jose.felix201@tectijuana.edu.mx}
+\and Mario García Valdez \at Tijuana Institute of Technology, Tijuana, Mexico, \email{mario@tectijuana.edu.mx}}
 %
@@
             in the population, making an improved distribution. It randomly selects a
-            solution from the elite set and uses the Golden Ratio to compute multiple
-            solutions against the best-found candidate.
+            solution from the elite set and uses the Golden Ratio 
+            \cite{nematollahi2020novel, gaikwad2021face, khesin2022golden, sym13081334, https://doi.org/10.1111/nyas.14895} 
+            to compute multiple solutions against the best-found candidate.
 

### 2022-09-30 paper.tex
first rev
Intro

@@
 \begin{document}
+\title{Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)}
+%
 
-\title*{Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)} 
 \titlerunning{Animal Life Cycle Algorithm (ALCA)}
@@
 % your contribution title if the original one is too long
-\author{J. C. Felix-Saul, Mario García Valdez}
+\author{J. C. Felix-Saul, Mario Garcia Valdez}
 % Use \authorrunning{Short Title} for an abbreviated version of
@@
     the more challenging the problem, the more computing power it will require
-    to solve them \cite{ontiveros2018high}. One technique to manage this
-    processing power is to use distributed computing
-    \cite{thain2005distributed} or the cloud available resources to help solve
-    the problem \cite{garcia2013there,eshratifar2019bottlenet}. This strategy
+    to solve them \cite{ontiveros2018high}. % You can add a comment on why it  
+    % requires more power, the main reason is the fitness evaluation function - M 
+    One technique to manage this
+    processing power is to use distributed computing % To manage the processing power need or demand? - M
+    \cite{thain2005distributed} or the cloud resources 
+    \cite{garcia2013there,eshratifar2019bottlenet}. This strategy
     allows adaptating the required computing power according to the problem's
@@
 
-    Most frequently, bio-inspired algorithms are developed with a sequential
+    Traditionally, bio-inspired algorithms are developed with a sequential
     (synchronous) perspective
     \cite{porto2018evolutionary,back1996evolutionary}, where a process must
-    pause for the previous job to finish before continuing. In this research,
+    pause for the previous task to finish before continuing.
+    % Add here a few current works that use the cloud and other distributed technologies - M
+    In this research,
     we present an algorithm built as a native cloud solution, totally
@@
 
-    In previous work, we introduced an algorithm inspired by the biological
+    In previous work, we introduced an algorithm inspired by the biological % Add the reference - M
     life-cycle of animal species. As in nature, population individuals grow older
@@
     either because of low fitness or age, causing occasional population extinction.
+    % Just to be sure explain a bit more what we mean by extinsion. - M
     When this condition presents itself, it is required to create a new population
-    to continue evolution (restart). We previously used to generate a new random
+    to continue evolution (restart). 
+    % Maybe you do it later, but explain what is a restart precisely 
+    We previously used to generate a new random % In a previous work (reference) - M
     set of solutions, with the cost of losing all evolution knowledge.
@@
     a distributed, parallel, and asynchronous methodology by algorithm
-    implementation and testing. We improve the algorithm behavior by solving
-    population extinction caused by nature's pressure in the Animal Life Cycle
+    implementation and testing.
+    % The main contribution is not this, is the restarting method? - M 
+    We improve the algorithm behavior by solving
+    population extinction caused by nature's pressure in the Animal Life Cycle % This is more a contribution - M
     Algorithm with one of the most promising alternatives: the projection of the
@@
 
-    We present the description of the following sections in our paper. First, we
+    We present the description of the following sections in our paper. First, we % This paper is organized as follows - M
+
     illustrate our algorithm model, the encountered problem with the occasional
@@
 %
-\bibliographystyle{splncs04}
+
+\bibliographystyle{splncs03_unsrt}
+%\bibliographystyle{splncs04}
 \bibliography{bib/bibliografia.bib}

### 2022-09-30 paper.tex
Proposal

@@
     In this research,
-    we present an algorithm built as a native cloud solution, totally
-    distributed, where its processes are executed asynchronously and in
+    we present a distributed algorithm built as a native cloud solution %, totally % fully, but this is hard to maintain - M
+    % distributed
+    , where its processes are executed asynchronously and in
     parallel. We designed the algorithm using the cloud available resources to
     distribute the processing workload among several computers or as a service
-    in the cloud. This strategy allows to elastically increase (or reduce) the
+    in the cloud. 
+    % The paragraph above is to repetitive, consider removing -  M
+    This strategy allows to elastically increase (or reduce) the
     computing power according to the nature of the challenge
@@
 
+    % If we are not going to add a State of the Art section, we need to mention other 
+    % methods in the Introduction. - M
 \section{Proposal}
     \label{section.proposal}
-    % Always give a unique label
-    % and use \ref{<label>} for cross-references
-    % and \cite{<label>} for bibliographic references
-    % use \sectionmark{}
-    % to alter or adjust the section heading in the running head
 
-    In previous work, we presented an algorithm inspired by nature, where we
-    used observation, analysis, and abstraction to model our algorithm based on
+    In previous work, we presented an algorithm inspired by nature, where we % Reference
+    % used observation, analysis, and abstraction to 
+    model our algorithm based on
     the generalization of the life cycle of animal species. Our algorithm, as
@@
     reproduction, and death. One key concept of our idea is that combining
-    those processes results in evolution. We propose to execute all these
+    those processes evolves the population. We propose to execute all these
     stages in parallel and asynchronously on a continuously evolving
@@
     \subsection{Algorithm Model}
+
+        % Start by stating the similarities with a GA, in the sense that 
+        % all individuals have a genotype (chromosome)that is a list of values.  - M
 
@@
         Figure~\ref{fig.algorithm_model}.
+        % I do not like that image, is not very clear. We are confused by the 
+        % similarity with Venn diagrams. Maybe is better to put boxes and arrows. - M
 
@@
     \subsection{Proposed Solution}
-
+        % It is important to do a literature review for the following papers, there are 
+        % other works that tackle similar problems or use it as a strategy. - M 
         In this article, we test various strategies to generate a new population to
@@
         strategy we describe in this paper uses elites to take advantage of the
+        % Where are the elites explained? - M
         historical evolution, especially the best individuals, where we look for the
@@
         ratio to compute the distance between new individuals in the population, making
-        an improved distribution.
+        an improved distribution. % Why is better? Explain. - M
 
@@
         projection of the historically best-found candidate solutions (Elite) towards
+        % Move the explanation of Elite to where we use the term for the first time - M
         the best-found candidate solution (Champion). This article proposes some
         strategies to carry out this operation, where the presented distribution
-        strategy obtained the best results.
+        strategy obtained the best results. % All this goes before they are mentioned. - M
 
-        \subsubsection{How does it work?}
+         % \subsubsection{How does it work?}
 
@@
             best-found candidate solutions (Elite) towards the best-found candidate
+            % You can use Elite now, we all now what it is. - M
             solution (Champion). To illustrate this concept we include

### 2022-09-30 paper.tex
Updated Changes
Work in progress.

@@
     the more challenging the problem, the more computing power it will require
-    to solve them \cite{ontiveros2018high}. % You can add a comment on why it  
-    % requires more power, the main reason is the fitness evaluation function - M 
+    to solve them \cite{ontiveros2018high}. We consider the main reason it requires 
+    more computing power is related to the evaluation of the fitness function, 
+    which means calculating the solution to the real problem our algorithm is searching for. 
     One technique to manage this
-    processing power is to use distributed computing % To manage the processing power need or demand? - M
+    processing power demand is to use distributed computing
     \cite{thain2005distributed} or the cloud resources 
-    \cite{garcia2013there,eshratifar2019bottlenet}. This strategy
-    allows adaptating the required computing power according to the problem's
-    complexity.
+    \cite{garcia2013there,eshratifar2019bottlenet}. This strategy allows adaptation 
+    of the required computing need according to the problem's complexity.
 
@@
     pause for the previous task to finish before continuing. 
-    % Add here a few current works that use the cloud and other distributed technologies - M
-    In this research,
-    we present a distributed algorithm built as a native cloud solution %, totally % fully, but this is hard to maintain - M
-    % distributed
-    , where its processes are executed asynchronously and in
-    parallel. We designed the algorithm using the cloud available resources to
-    distribute the processing workload among several computers or as a service
-    in the cloud. 
-    % The paragraph above is to repetitive, consider removing -  M
+    Some architectures address this issue \cite{valdez2021container,garcia2015evospace,merelo2016nodio} 
+    by working on the cloud and finding solutions on distributed technologies.
+    In this research, we present a distributed algorithm totally built as a 
+    native cloud solution, where its processes execute asynchronously and in 
+    parallel, managing the processing workload among several computers.  
     This strategy allows to elastically increase (or reduce) the
@@
     In previous work, we introduced an algorithm inspired by the biological % Add the reference - M
-    life-cycle of animal species. As in nature, population individuals grow older
+    life-cycle of animal species. As in nature, population individuals grow older % \cite{Felix-Saul2022}
     and age. In this algorithm's reproduction process, couples must match by mutual

### 2022-09-30 paper.tex
Updated Paper
Work in progress.

@@
 
-    The main contribution of this paper is to demonstrate that it is possible to
-    evolve a population of individuals, similar to a Genetic Algorithm (GA), using
-    a distributed, parallel, and asynchronous methodology by algorithm
+    One contribution of this paper is to demonstrate that it is possible to
+    evolve a population of individuals, similar to a Genetic Algorithm (GA),
+    using a distributed, parallel, and asynchronous methodology by algorithm
     implementation and testing.
-    % The main contribution is not this, is the restarting method? - M 
-    We improve the algorithm behavior by solving
-    population extinction caused by nature's pressure in the Animal Life Cycle % This is more a contribution - M
-    Algorithm with one of the most promising alternatives: the projection of the
-    Elite towards the Champion, where we compare the results obtained with the
-    latter and the random use of the more traditional alternatives (mutation and
-    crossover), using classic benchmark functions for optimization for comparison.
 
-    We present the description of the following sections in our paper. First, we % This paper is organized as follows - M
+    The main contribution of this research is to demonstrate how to improve the
+    algorithm's behavior, by solving population extinction caused by nature's
+    pressure in the Animal Life Cycle Algorithm with one of the most promising
+    alternatives: the projection of the Elite towards the Champion. To validate
+    our findings, we compare the results obtained with the latter and the
+    random use of the more traditional alternatives (mutation and crossover),
+    using classic benchmark functions for optimization for comparison.
 
+    This paper is organized as follows. First, we 
     illustrate our algorithm model, the encountered problem with the occasional
@@
     In previous work, we presented an algorithm inspired by nature, where we % Reference
-    % used observation, analysis, and abstraction to 
     model our algorithm based on
@@
         strategy obtained the best results. % All this goes before they are mentioned. - M
-
-         % \subsubsection{How does it work?}
 

### 2022-09-30 paper.tex
Updated References
Work in progress. Still missing previous work.

@@
     In previous work, we introduced an algorithm inspired by the biological % Add the reference - M
-    life-cycle of animal species. As in nature, population individuals grow older % \cite{Felix-Saul2022}
+    life-cycle of animal species \cite{Felix-Saul2022}. As in nature, population individuals grow older
     and age. In this algorithm's reproduction process, couples must match by mutual
@@
 
-    In previous work, we presented an algorithm inspired by nature, where we % Reference
-    model our algorithm based on
+    In previous work, we presented an algorithm inspired by nature 
+    \cite{Felix-Saul2022}, where we model our algorithm based on
     the generalization of the life cycle of animal species. Our algorithm, as
@@
 \bibliography{bib/bibliografia.bib}
+%\bibliography{10.1007_978-3-031-08266-5_8-citation.bib}
 
@@
 
-% TO-DO: Turniting.
+% TO-DO: Turnitin.

### 2022-09-30 paper.tex
Updated Document
Work in progress.

@@
 
-    In previous work, we introduced an algorithm inspired by the biological % Add the reference - M
+    In previous work, we introduced an algorithm inspired by the biological
     life-cycle of animal species \cite{Felix-Saul2022}. As in nature, population individuals grow older
@@
     % Maybe you do it later, but explain what is a restart precisely 
-    We previously used to generate a new random % In a previous work (reference) - M
+    In a previous work \cite{Felix-Saul2022} we used to generate a new random
     set of solutions, with the cost of losing all evolution knowledge.
@@
 
-        % Start by stating the similarities with a GA, in the sense that 
-        % all individuals have a genotype (chromosome)that is a list of values.  - M
+        This algorithm was inspired by the traditional Genetic Algorithm,
+        meaning that all individuals have a genotype (chromosome) that is a
+        list of values. We calculate the individual's fitness with the
+        evaluation function and do crossover and mutation to the population.
+        What makes our strategy different is that we don't use the concept of
+        evolutionary generations. We manage our set of solutions as a whole
+        that continuously evolve over time. Allowing individuals of different
+        ages to breed and generate offspring, as it happens in nature. The
+        crossover and mutation execute as independent processes that randomly
+        affect the individuals.
 

### 2022-10-01 paper.tex
Updated Paper
Work in progress.

@@
         aptitude, as happens in the life cycle. We previously used to generate a new
-        random set of solutions, with the cost of losing all evolution knowledge. The
-        strategy we describe in this paper uses elites to take advantage of the
-        % Where are the elites explained? - M
-        historical evolution, especially the best individuals, where we look for the
-        offspring of the elite set to be somewhat close to them. We use the golden
-        ratio to compute the distance between new individuals in the population, making
+        random set of solutions, with the cost of losing all evolution knowledge.
+
+        This article proposes some strategies to carry out this operation,
+        where the presented distribution strategy obtained the best results. We
+        propose one promising alternative to restart the population, to solve
+        extinction caused by nature's pressure in the Life Cycle algorithm: the
+        projection of the historically best-found candidate solutions (Elite)
+        towards the best-found candidate solution (Champion).
+
+        The strategy we describe in this paper use an elite set, that includes
+        the historically best-found candidate solutions to take
+        advantage of the historical evolution. Our goal is for the offspring to
+        be somewhat close to the best individuals of the Elite.
+        We use the golden ratio to compute the distance between new individuals in the population, making
         an improved distribution. % Why is better? Explain. - M
-
-        We propose one promising alternative to restart the population, to solve
-        extinction caused by nature's pressure in the Life Cycle algorithm: the
-        projection of the historically best-found candidate solutions (Elite) towards
-        % Move the explanation of Elite to where we use the term for the first time - M
-        the best-found candidate solution (Champion). This article proposes some
-        strategies to carry out this operation, where the presented distribution
-        strategy obtained the best results. % All this goes before they are mentioned. - M
 
@@
 
-        This strategy is how we can calculate the projection of the historically
-        best-found candidate solutions (Elite) towards the best-found candidate
-        % You can use Elite now, we all now what it is. - M
-        solution (Champion). To illustrate this concept we include
-        Figure~\ref{fig.elite_projection}, placing the Elite solution on the far right
-        and the Champion solution on the left corner, where a higher number of new
-        solutions will be closer to the Champion.
+        This strategy is how we can calculate the projection of the
+        historically Elite towards the Champion solution. To illustrate this
+        concept, we include Figure~\ref{fig.elite_projection}, placing the
+        Elite solution on the far right and the Champion solution on the left
+        corner. We can observe the higher amount of new solutions progressively
+        closer to the Champion.
 

### 2022-10-01 paper.tex
Updated Paper
Work in progress.

@@
     either because of low fitness or age, causing occasional population extinction.
-    % Just to be sure explain a bit more what we mean by extinsion. - M
-    When this condition presents itself, it is required to create a new population
-    to continue evolution (restart). 
+
+    We define extinction as a situation in which something no longer exists; in
+    our case scenario, when we refer to extinction in our algorithm, it means
+    the population of individuals no longer exists. When this condition
+    presents itself, it is required to create a new population to continue
+    evolution (restart).
+
     % Maybe you do it later, but explain what is a restart precisely 
@@
         We use the golden ratio to compute the distance between new individuals in the population, making
-        an improved distribution. % Why is better? Explain. - M
+        an improved distribution. We can consider our strategy an improvement 
+        over other alternatives because of the findings of our latter experiments.
 

### 2022-10-01 paper.tex
Updated Paper
Work in progress.

@@
     presents itself, it is required to create a new population to continue
-    evolution (restart).
+    evolution (restart). Population restart is the process in which we create a
+    new set of individuals to replace the others that have already died (or
+    were discarded) due to their aptitude. In a previous work
+    \cite{Felix-Saul2022} we used to generate a new random set of solutions,
+    with the cost of losing all evolution knowledge.
 
-    % Maybe you do it later, but explain what is a restart precisely 
-    In a previous work \cite{Felix-Saul2022} we used to generate a new random
-    set of solutions, with the cost of losing all evolution knowledge.
-
-    One contribution of this paper is to demonstrate that it is possible to
+    One contribution of this paper is to proof that it is possible to
     evolve a population of individuals, similar to a Genetic Algorithm (GA),

### 2022-10-01 paper.tex
Updated Paper
Work in progress.

@@
 
-    One contribution of this paper is to proof that it is possible to
+    One contribution of this paper is to prove that it is possible to
     evolve a population of individuals, similar to a Genetic Algorithm (GA),

### 2022-10-01 paper.tex
Updated Model
Updated algorithm model figure.
Updated Model
Updatec Algorithm Model Image
Updated Paper
Population restart references updated.

@@
     presents itself, it is required to create a new population to continue
-    evolution (restart). Population restart is the process in which we create a
+    evolution (restart).
+
+    Population restart is the process in which we create a
     new set of individuals to replace the others that have already died (or
-    were discarded) due to their aptitude. In a previous work
-    \cite{Felix-Saul2022} we used to generate a new random set of solutions,
-    with the cost of losing all evolution knowledge.
+    were discarded) due to their aptitude. In a previous work \cite{Felix-Saul2022} 
+    we used to generate a new random set of solutions, with the cost of losing 
+    all evolution knowledge. In the state of the art, we have found other methodologies 
+    that have successfully sought to solve the problem of population extinction with
+    restarts \cite{hellwig2020modified, loshchilov2013cma, jansen2010aging, tendresse2001effects, mathias1998effects}.
 
@@
 
-    % If we are not going to add a State of the Art section, we need to mention other 
-    % methods in the Introduction. - M
 \section{Proposal}
@@
         Figure~\ref{fig.algorithm_model}.
-        % I do not like that image, is not very clear. We are confused by the 
-        % similarity with Venn diagrams. Maybe is better to put boxes and arrows. - M
 
@@
             \centering
-            \includegraphics[width=80mm]{img/fig_algorithm_model.pdf}
+            \includegraphics[width=100mm]{img/fig_algorithm_model.pdf}
             \caption{Animal Life Cycle Algorithm model.} \label{fig.algorithm_model}

### 2022-10-01 paper.tex
Updated Paper
Fixed Error label to Best-found error average

@@
         For each experiment, we ran 30 independent executions per algorithm and
-        dimensions specified. We recorded the following results: best found error,
+        dimensions specified. We recorded the following results: best-found error average,
         standard deviation, total number of evaluations, and total elapsed time (in
@@
         \begin{itemize}
-            \item   Error:       is the best found error (or best solution).
+            \item   Error:       is the best-found error average.
             \item   St-Dev:      is the standard deviation calculated from the error. 

### 2022-10-02 paper.tex
Updated Paper
Numeric index fix.
Updated Equation
Golden Ratio Equation Fix

@@
 \begin{document}
-\title{Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)}
+\title*{Recovering from population extinction in the Animal Life Cycle Algorithm (ALCA)}
 %
@@
         solution and the elite set, we use the Golden Ratio (shown in
-        Figure~\ref{fig.golden_ratio}) to compute the distance between new individuals
+        Equation~\ref{eq.golden_ratio}) to compute the distance between new individuals
         in the population, making an improved distribution. It randomly selects a
@@
 
-        \begin{figure}
+        \begin{equation}
             \centering
-            \includegraphics[width=25mm]{img/fig_golden_ratio.pdf}
-            \caption{Golden Ratio equation.} \label{fig.golden_ratio}
-            \end{figure}
+            \begin{matrix}\includegraphics[width=25mm]{img/eq_golden_ratio.pdf}\end{matrix}
+            \label{eq.golden_ratio}
+            \end{equation}
 

### 2022-10-02 paper.tex
Updated Paper
Equation Fix
Updated Reference
First Publication Reference Fixed
Updated Info
Basic proyect info updated.

@@
 % your contribution title if the original one is too long
-\institute{J. C. Felix-Saul \at Tijuana Institute of Technology, Tijuana, Mexico, \email{jose.felix201@tectijuana.edu.mx}
-\and Mario García Valdez \at Tijuana Institute of Technology, Tijuana, Mexico, \email{mario@tectijuana.edu.mx}}
+\institute{J. C. Felix-Saul \at TecNM, Tijuana Institute of Technology, Tijuana, Mexico, \email{jose.felix201@tectijuana.edu.mx}
+\and Mario García Valdez \at TecNM, Tijuana Institute of Technology, Tijuana, Mexico, \email{mario@tectijuana.edu.mx}}
 %
@@
         \begin{equation}
-            \centering
             \begin{matrix}\includegraphics[width=25mm]{img/eq_golden_ratio.pdf}\end{matrix}
@@
 \begin{acknowledgement}
-    This paper has been supported in part by projects DeepBio (TIN2017--85727--C4--2--P) and TecNM Project 11356.21\@.
+    This paper has been supported in part by TecNM Project 15340.22-P.
 \end{acknowledgement}
@@
 \bibliography{bib/bibliografia.bib}
-%\bibliography{10.1007_978-3-031-08266-5_8-citation.bib}
 
